%%%%%% rcsid = @(#)$Id: sample-sb.tex,v 1.21 2007/02/04 04:14:21 rathc Exp $
%%%%%%
%%
%%      ===============================
%%      Sample Songbook (sample-sb.tex)
%%      ===============================
%%
%%      Version 4.3, 02 February, 2007
%%
%%      Copyright 1992--2007 Christopher Rath <christopher@rath.ca>
%%
%%      This package is free software; you can redistribute it and/or
%%      modify it under the terms of version 2.1 of the GNU Lesser
%%  General Public License as published by the Free Software
%%  Foundation.
%%
%%      This package is distributed in the hope that it will be
%%      useful, but WITHOUT ANY WARRANTY; without even the implied
%%      warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
%%      PURPOSE.  See the GNU Lesser General Public License for more
%%      details.
%%
%%      This file contains a subset of the songbook we distribute
%%      at our church.  To the best of my knowledge, all of the lyrics
%%      contained herein are freely distributable.  This file has been
%%      provided as a sample of what can be produced by the chordbk,
%%      wordbk, and overhead LaTeX styles.
%%
%%      NEEDED:  The fancyhdr LaTeX style is required to properly
%%              format this file.  If you don't have that then comment
%%              out the commands in the preamble which deal with the
%%              fancyhdr style.
%%
%%%%%%
%%%%%%
%%
%%      1. Chord notation.  Within this songbook the following
%%         conventions have been adopted:
%%
%%              "Minor" is entered as "m";
%%                      e.g. Cm7 for C minor 7th.
%%              "Major" is entered as "M";
%%                      e.g. CM7 for C major 7th.
%%
%%%%%%
%%%%%%
%%      ============
%%      Bibliography
%%      ============
%%
%%      Exalt Him!: Exalt Him!  Compiled by Tom Fettke.  (c)1989
%%                      Word Music.
%%
%%      Hosanna! Music Books: Hosanna! Music Books #1--#6.
%%                      (c)1987--92 Integrity Music, Inc.
%%
%%      Worship Him II: Worship Him II.  Compiled by Jesse Peterson
%%                      and Bruce Ballinger.  (c)1989 Tempo Music
%%                      Publications.
%%
%%      Worship Songs Of The Vineyard: Worship Songs Of The Vineyard
%%                      --- Volume 2.  (c)1989 Vineyard Ministries
%%                      International.
%%
%%%%%%
%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                      %%
%%           P R E A M B L E   B E G I N S              %%
%%                                                      %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{book}
\usepackage{latexsym,fancyhdr}
\usepackage{hyperref}

% Custom command for song index hyperlinks - makes entire entry clickable
\newcommand{\sbindexitem}[2]{\item \hyperlink{song#2}{#1,~#2}}
%%\usepackage[chordbk]{songbook}                  %% Words & Chords edition.
%%\usepackage[compactsong,chordbk]{songbook}    %% Words & Chords edition.
\usepackage[wordbk]{songbook}                 %% Words Only edition.
%%\usepackage[overhead]{songbook}               %% Overhead
% Transparency edition.

%%%
% Revision Date and Release Date definitions.
%
%       \RelDate - The last time this songbook was released.  Set this
%                  date each time a new release/update of the songbook
%                  is generated.
%       \RevDate - The last time a particular song was revised in any
%                  way.  This command will be renewed inside every
%                  song.
%%%
\newcommand{\RelDate}{31~December,~2025}
\newcommand{\RevDate}{\today}

%%%
% C.C.L.I. license number definition; for copyright licensing info.
% One of these macros will be manually inserted into the {CpyRt}
% parameter of the {song} environment.
%
%       \CCLInumber - The actual copyright license number.  Don't
%               insert this command in the {CpyRt} parameter, use one
%               of the others.
%       \CCLIed - Indicates a song falls under our CCLI license.
%       \NotCCLIed - Indicates a song doesn't fall under our CCLI
%               license.  Public Domain songs fall into this category.
%       \PGranted - We have received specific permission from the
%               copyright holder to use this song.
%       \PPending - We are in the process of obtaining permission to
%               use this song.
%%%
\newcommand{\CCLInumber}{Your CCLI Number}
\newcommand{\CCLIed}{{\CpyRtInfoFont (CCLI \CCLInumber)}}
\newcommand{\NotCCLIed}{\relax}
\newcommand{\PGranted}{\relax}
\newcommand{\PPending}{{\CpyRtInfoFont (Permission Pending)}}

%%%
% Title page information.
%%%
\title{Melbourne Songs}
% \author{TS}
\date{Last Revised:  \RevDate}

%%%
% Redefine fonts from SongBook style that I don't like.
%%%
\font\myTinySF=cmss8 at 8pt
\renewcommand{\CpyRtInfoFont}{\tiny\myTinySF}

%%%
% Define fonts to use in the headers and footers of the songbook.
%%%
\newcommand{\LHeadFont}{\normalsize}            % = cmr12  at 12pt
\newcommand{\CHeadFont}{\normalsize\rm}         % = cmr12  at 12pt
\newcommand{\RHeadFont}{\normalsize}            % = cmr12  at 12pt
\newcommand{\LFootFont}{\scriptsize}            % = cmr8   at  8pt
\newcommand{\CFootFont}{\tiny\myTinySF}         % = cmss8  at  8pt
\newcommand{\RFootFont}{\scriptsize}            % = cmr8   at  8pt

%%%
% Turn on and define fancy page heading/footing definition.
%%%
\pagestyle{fancy}

\ifChordBk
% It's a words & chords songbook...
\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{\marginparwidth}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[LE,RO]{\LHeadFont\emph{\leftmark\/}\SBContinueMark}
\fancyhead[CE,CO]{\CHeadFont\thepage}
\fancyhead[RE,LO]{\RHeadFont\RelDate}
\else\ifOverhead
% It's an overhead...
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[LE,RO]{}
\fancyhead[CE,CO]{}
\fancyhead[RE,LO]{}
\else\ifWordBk
% It's a words only songbook...
\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{\marginparwidth}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[LE,RO]{\LHeadFont Melbourne Songs}
\fancyhead[CE,CO]{\CHeadFont\thepage}
\fancyhead[RE,LO]{\RHeadFont\RelDate}
\fi\fi\fi

\fancyfoot[L]{\LFootFont v0.1 // please reach out for corrections}
\fancyfoot[R]{\LFootFont\hyperlink{songindex}{Back to Index}}
% \ifSongEject
% \fancyfoot[CE,CO]{\CFootFont Last Revised:  \RevDate}
% \else
% \fancyfoot[CE,CO]{\CFootFont}
% \fi
% \fancyfoot[RE,LO]{\RFootFont Material used by permission.}

%%%
% Turn on/off index-file generation.  Uncomment the \makeindex line to
% turn index generation on;  comment it out to turn index generation
% off.
%%%
\makeTitleIndex         %% Title and First Line Index.
% \makeTitleContents      %% Table of Contents.
% \makeKeyIndex           %% Index of song by key.
% \makeArtistIndex  %% Index of song by artist.

\newcommand{\WBColBrk}{%
  \ifWordBk%
  \newpage%
\fi}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                      %%
%%           D O C U M E N T   B E G I N S              %%
%%                                                      %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%
% Uncomment "\maketitle" statement to make a title page.
%%%
\maketitle

\newpage
% \section*{Title Index}
\hypertarget{songindex}{}
\begin{theindex}
  \input{melbourne-songs.tdx}
\end{theindex}

\mainmatter
\ifWordBk
\twocolumn
\fi

%%%
% Songbook begins.
%%%
% \begin{song}{Nothing But The Blood}{D}
%   {\SBPubDom}
%   {Robert Lowry}
%   {Ephesians~1:7}
%   {\NotCCLIed}

%   \renewcommand{\RevDate}{February~11,~1993}
%   \SBRef{Hosanna! Music Book~I}{\#65}
%   \FLineIdx{What can wash away my sin}

%   \begin{SBVerse}
%     \Ch{D}{What} can wash a\Ch{F#m}{way} my \Ch{Bm}{sin?}

%     \Ch{G}{Noth}ing but the \Ch{D}{blood} of \Chr{A7}{Je}\Ch{D}{sus.}

%     \Ch{D}{What} can make me \Ch{F#m}{whole} a\Ch{Bm}{gain?}

%     \Ch{G}{Noth}ing but the \Ch{D}{blood} of \Chr{A7}{Je}\Ch{D}{sus.}
%   \end{SBVerse}

%   \begin{SBOpGroup}
%     \Ch{D}{Oh,} Precious \Ch{F#m}{is} the \Ch{Bm}{flow}

%     \Ch{G}{That} \Ch{Em}{makes} me \Ch{A}{white} as \Ch{D}{snow.}\Ch{A7}{}

%     \Ch{D}{No} other \Ch{F#m}{fount} I \Ch{Bm}{know,}

%     \Ch{G}{Noth}ing but the \Ch{D}{blood} of \Chr{A7}{Je}\Ch{D}{sus.}
%   \end{SBOpGroup}

%   \begin{SBVerse}
%     \Ch{D}{This} is all my \Ch{F#m}{righteous}\Ch{Bm}{ness,}

%     \Ch{G}{Noth}ing but the \Ch{D}{blood} of \Chr{A7}{Je}\Ch{D}{sus.}

%     \Ch{D}{This} is all my \Ch{F#m}{hope} and \Ch{Bm}{peace,}

%     \Ch{G}{Noth}ing but the \Ch{D}{blood} of \Chr{A7}{Je}\Ch{D}{sus.}
%   \end{SBVerse}

%     \begin{SBVerse}
%     \Ch{D}{This} is all my \Ch{F#m}{righteous}\Ch{Bm}{ness,}

%     \Ch{G}{Noth}ing but the \Ch{D}{blood} of \Chr{A7}{Je}\Ch{D}{sus.}

%     \Ch{D}{This} is all my \Ch{F#m}{hope} and \Ch{Bm}{peace,}

%     \Ch{G}{Noth}ing but the \Ch{D}{blood} of \Chr{A7}{Je}\Ch{D}{sus.}
%   \end{SBVerse}
% \end{song}

\begin{song}{Dear Savior, Thou art mine}{D}
  {}
  {}
  {}
  {}

  \renewcommand{\RevDate}{February~11,~1993}
  \SBRef{Hosanna! Music Book~I}{\#65}

  \begin{SBVerse}
    Dear Savior, Thou art mine,

    How sweet the thought to me;

    Let me repeat Thy name,

    And lift my heart to Thee.
  \end{SBVerse}

  \begin{SBOpGroup}
    Mine! Mine! Mine!
    I know Thou art mine;
    Savior, dear Savior,
    I know Thou art mine.

  \end{SBOpGroup}

  \begin{SBVerse}
    Thou art the sinner’s friend,
    So I Thy friendship claim,
    A sinner saved by grace,
    When Thy sweet message came.
  \end{SBVerse}

  \begin{SBVerse}
    My hardened heart was touched;
    Thy pard’ning voice I heard;
    And joy and peace came in
    While list’ning to Thy word.
  \end{SBVerse}

  \begin{SBVerse}

    So let me sing Thy praise,
    So let me call Thee mine.
    I cannot doubt Thy word,
    I know that I am Thine.
  \end{SBVerse}
\end{song}

\begin{song}{A Mind At Perfect Peace With God}{G}
  {\SBPubDom}
  {Horatius Bonar}
  {}
  {}

  \begin{SBVerse}
    A mind at perfect peace with God;

    O what a word is this!

    A sinner reconciled through blood;

    This, this indeed is peace.
  \end{SBVerse}

  \begin{SBVerse}
    By nature and by practice far,

    How very far from God;

    Yet now by grace brought nigh to Him,

    Through faith in Jesus' blood.
  \end{SBVerse}

  \begin{SBVerse}
    So nigh, so very nigh to God,

    I cannot nearer be;

    For in the person of His Son

    I am as near as He.
  \end{SBVerse}

  \begin{SBVerse}
    So dear, so very dear to God,

    More dear I cannot be;

    The love wherewith He loves the Son,

    Such is His love to me.
  \end{SBVerse}

  \begin{SBVerse}
    Why should I ever anxious be,

    Since such a God is mine?

    He watches o'er me night and day,

    And tells me ``Mine is thine.''
  \end{SBVerse}
\end{song}

\begin{song}{He Hideth My Soul}{}
  {\SBPubDom}
  {Fanny Crosby}
  {}
  {}

  \begin{SBVerse}
    A wonderful Savior is Jesus my Lord,

    A wonderful Savior to me;

    He hideth my soul in the cleft of the rock,

    Where rivers of pleasure I see.
  \end{SBVerse}

  \begin{SBOpGroup}
    He hideth my soul in the cleft of the rock

    That shadows a dry, thirsty land;

    He hideth my life in the depths of His love,

    And covers me there with His hand,

    And covers me there with His hand.
  \end{SBOpGroup}

  \begin{SBVerse}
    A wonderful Savior is Jesus my Lord,

    He taketh my burden away;

    He holdeth me up and I shall not be moved,

    He giveth me strength as my day.
  \end{SBVerse}

  \begin{SBVerse}
    With numberless blessings each moment He crowns,

    And, filled with His fulness divine,

    I sing in my rapture, oh, glory to God,

    For such a Redeemer as mine!
  \end{SBVerse}

  \begin{SBVerse}
    When clothed in His brightness, transported I rise

    To meet Him in clouds of the sky,

    His perfect salvation, His wonderful love,

    I'll shout with the millions on high.
  \end{SBVerse}
\end{song}

\begin{song}{Redemption Ground}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Come sing, my soul, and praise the Lord,

    Who hath redeemed thee by His blood;

    Delivered thee from chains that bound,

    And brought thee to redemption ground.
  \end{SBVerse}

  \begin{SBOpGroup}
    Redemption ground, the ground of peace!

    Redemption ground, O wondrous grace!

    Here let our praise to God abound!

    Who saves us on redemption ground.
  \end{SBOpGroup}

  \begin{SBVerse}
    Once from my God I wandered far,

    And with His holy will made war;

    But now my songs to God abound;

    I'm standing on redemption ground.
  \end{SBVerse}

  \begin{SBVerse}
    O joyous hour! when God to me

    A vision gave of Calvary;

    My bonds were loos'd---my soul unbound,

    I sang upon redemption ground.
  \end{SBVerse}

  \begin{SBVerse}
    No works of merit now I plead,

    But Jesus take, for all my need;

    No righteousness in me is found,

    Except upon redemption ground.
  \end{SBVerse}

  \begin{SBVerse}
    Come, weary soul, and here find rest;

    Accept redemption, and be blest:

    The Christ who died, by God is crowned

    To pardon on redemption ground.
  \end{SBVerse}
\end{song}

\begin{song}{Day By Day}{}
  {\SBPubDom}
  {Lina Sandell}
  {}
  {}

  \begin{SBVerse}
    Day by day, and with each passing moment,

    Strength I find to meet my trials here;

    Trusting in my Father's wise bestowment,

    I've no cause for worry or for fear.

    He, whose heart is kind beyond all measure,

    Gives unto each day what He deems best,

    Lovingly its part of pain and pleasure,

    Mingling toil with peace and rest.
  \end{SBVerse}

  \begin{SBVerse}
    Every day the Lord Himself is near me,

    With a special mercy for each hour;

    All my cares He fain would bear and cheer me,

    He whose name is Counsellor and Pow'r.

    The protection of His child and treasure

    Is a charge that on Himself He laid;

    ``As thy days, thy strength shall be in measure,''

    This the pledge to me He made.
  \end{SBVerse}

  \begin{SBVerse}
    Help me then, in every tribulation,

    So to trust Thy promises, O Lord,

    That I lose not faith's sweet consolation,

    Offered me within Thy holy Word.

    Help me, Lord, when toil and trouble meeting,

    E'er to take, as from a father's hand,

    One by one, the days, the moments fleeting,

    Till with Christ the Lord I stand.
  \end{SBVerse}
\end{song}

\begin{song}{That Man Of Calvary}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Fairest of all the earth beside,

    Chiefest of all unto Thy bride,

    Fulness divine in Thee I see;

    Beautiful Man of Calvary!
  \end{SBVerse}

  \begin{SBOpGroup}
    That Man who died on Calvary

    Has cleansed my heart and set me free;

    Sin's power no more can fetter me

    Since Jesus died on Calvary.
  \end{SBOpGroup}

  \begin{SBVerse}
    Drinking a dire and dreadful cup,

    Crucified Jesus lifted up,

    Bearing our guilt and misery;

    Sorrowful Man of Calvary!
  \end{SBVerse}

  \begin{SBVerse}
    Granting the sinner life and peace,

    Granting the captive sweet release,

    Shedding His blood to make us free;

    Merciful Man of Calvary!
  \end{SBVerse}

  \begin{SBVerse}
    Gather'd with Thee eternally,

    Sharing Thy love by glassy sea,

    Like Thee forever I shall be;

    Glorified Man of Calvary!
  \end{SBVerse}
\end{song}

\begin{song}{Draw Me Nearer}{}
  {\SBPubDom}
  {Fanny Crosby}
  {}
  {}

  \begin{SBVerse}
    I am Thine, O Lord, I have heard Thy voice,

    And it told Thy love to me;

    But I long to rise in the arms of faith,

    And be closer drawn to Thee.
  \end{SBVerse}

  \begin{SBOpGroup}
    Draw me nearer, nearer, blessed Lord,

    To the cross where Thou hast died;

    Draw me nearer, nearer, nearer, blessed Lord,

    To Thy precious, bleeding side.
  \end{SBOpGroup}

  \begin{SBVerse}
    Consecrate me now to Thy service, Lord,

    By the pow'r of grace divine;

    Let my soul look up with a steadfast hope,

    And my will be lost in Thine.
  \end{SBVerse}

  \begin{SBVerse}
    O the pure delight of a single hour

    That before Thy throne I spend,

    When I kneel in prayer, and with Thee, my God,

    I commune as friend with friend!
  \end{SBVerse}

  \begin{SBVerse}
    There are depths of love that I cannot know

    Till I cross the narrow sea;

    There are heights of joy that I may not reach

    Till I rest in peace with Thee.
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{I Heard The Voice Of Jesus Say}{}
  {\SBPubDom}
  {Horatius Bonar}
  {}
  {}

  \begin{SBVerse}
    I heard the voice of Jesus say,

    ``Come unto Me and rest;

    Lay down, O weary one, lay down

    Thy head upon My breast.''

    I came to Jesus as I was,

    Weary, and worn, and sad;

    I found in Him a resting-place,

    And He has made me glad.
  \end{SBVerse}

  \begin{SBVerse}
    I heard the voice of Jesus say,

    ``Behold, I freely give

    The living water; thirsty one,

    Stoop down, and drink, and live.''

    I came to Jesus, and I drank

    Of that life-giving stream;

    My thirst was quench'd, my soul revived,

    And now I live in Him.
  \end{SBVerse}

  \begin{SBVerse}
    I heard the voice of Jesus say,

    ``I am this dark world's Light;

    Look unto Me, your morn shall rise,

    And all your day be bright.''

    I looked to Jesus, and I found

    In Him my Star, my Sun;

    And in that Light of life I'll walk,

    Till trav'ling days are done.
  \end{SBVerse}
\end{song}

\begin{song}{In The Garden}{}
  {\SBPubDom}
  {C. Austin Miles}
  {}
  {}

  \begin{SBVerse}
    I come to the garden alone,

    While the dew is still on the roses;

    And the voice I hear, falling on my ear,

    The Son of God discloses.
  \end{SBVerse}

  \begin{SBOpGroup}
    And He walks with me, and He talks with me,

    And He tells me I am His own,

    And the joy we share as we tarry there,

    None other has ever known.
  \end{SBOpGroup}

  \begin{SBVerse}
    He speaks, and the sound of His voice

    Is so sweet the birds hush their singing;

    And the melody that He gave to me

    Within my heart is ringing.
  \end{SBVerse}

  \begin{SBVerse}
    I'd stay in the garden with Him

    Tho' the night around me be falling;

    But He bids me go; thro' the voice of woe,

    His voice to me is calling.
  \end{SBVerse}
\end{song}

% \WBPageBrk

\begin{song}{I Have A Shepherd}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    I have a Shepherd, One I love so well;

    How He has blessed me tongue can never tell;

    On the cross He suffered, shed His blood and died,

    That I might ever in His love confide.
  \end{SBVerse}

  \begin{SBOpGroup}
    Following Jesus, ever day by day,

    Nothing can harm me when He leads the way;

    Darkness or sunshine, whate'er befall---

    Jesus, the Shepherd, is my All in All.
  \end{SBOpGroup}

  \begin{SBVerse}
    Pastures abundant doth His hand provide,

    Still waters flowing ever at my side,

    Goodness and mercy follow on my track,

    With such a Shepherd nothing can I lack.
  \end{SBVerse}

  \begin{SBVerse}
    When I would wander from the path astray,

    Then He will draw me back into the way;

    In the darkest valley I need fear no ill,

    For He, my Shepherd, will be with me still.
  \end{SBVerse}
\end{song}

\begin{song}{I Need Thee Every Hour}{}
  {\SBPubDom}
  {Annie S. Hawks}
  {}
  {}

  \begin{SBVerse}
    I need Thee ev'ry hour,

    Most gracious Lord;

    No tender voice like Thine

    Can peace afford.
  \end{SBVerse}

  \begin{SBOpGroup}
    I need Thee, O I need Thee;

    Ev'ry hour I need Thee;

    O bless me now, my Savior,

    I come to Thee.
  \end{SBOpGroup}

  \begin{SBVerse}
    I need Thee ev'ry hour,

    Stay Thou nearby;

    Temptations lose their pow'r

    When Thou art nigh.
  \end{SBVerse}

  \begin{SBVerse}
    I need Thee ev'ry hour,

    In joy or pain;

    Come quickly and abide,

    Or life is vain.
  \end{SBVerse}

  \begin{SBVerse}
    I need Thee ev'ry hour,

    Teach me Thy will;

    And Thy rich promises

    In me fulfill.
  \end{SBVerse}

  \begin{SBVerse}
    I need Thee ev'ry hour,

    Most Holy One;

    O make me Thine indeed,

    Thou blessed Son.
  \end{SBVerse}
\end{song}

\begin{song}{I Will Sing The Wondrous Story}{}
  {\SBPubDom}
  {Francis H. Rowley}
  {}
  {}

  \begin{SBVerse}
    I will sing the wondrous story

    Of the Christ who died for me.

    How He left His home in glory

    For the cross of Calvary.

    I was lost, but Jesus found me,

    Found the sheep that went astray,

    Threw His loving arms around me,

    Drew me back into His way.
  \end{SBVerse}

  \begin{SBVerse}
    I was bruised, but Jesus healed me;

    Faint was I from many a fall;

    Sight was gone, and fears possessed me,

    But He freed me from them all.

    Days of darkness still come o'er me,

    Sorrow's paths I often tread,

    But the Savior still is with me;

    By His hand I'm safely led.
  \end{SBVerse}

  \begin{SBVerse}
    He will keep me till the river

    Rolls its waters at my feet;

    Then He'll bear me safely over,

    Where the loved ones I shall meet.

    Yes, I'll sing the wondrous story

    Of the Christ who died for me,

    Sing it with the saints in glory,

    Gathered by the crystal sea.
  \end{SBVerse}
\end{song}

\begin{song}{I'm Not Ashamed To Own My Lord}{}
  {\SBPubDom}
  {Isaac Watts}
  {}
  {}

  \begin{SBVerse}
    I'm not ashamed to own my Lord,

    Or to defend His cause,

    Maintain the honour of His Word,

    The glory of His cross.
  \end{SBVerse}

  \begin{SBOpGroup}
    At the cross! at the cross! where I first saw the light,

    And the burden of my heart rolled away;

    It was there by faith I received my sight,

    And now I am happy all the day!
  \end{SBOpGroup}

  \begin{SBVerse}
    Jesus, my God! I know His name,

    His name is all my trust;

    Nor will He put my soul to shame,

    Nor let my hope be lost.
  \end{SBVerse}

  \begin{SBVerse}
    Firm as His throne His promise stands,

    And He can well secure

    What I've committed to His hands,

    Till the decisive hour.
  \end{SBVerse}

  \begin{SBVerse}
    Then will He own my worthless name

    Before His Father's face;

    And, in the New Jerusalem,

    Appoint my soul a place.
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{I've Found A Friend In Jesus}{}
  {\SBPubDom}
  {Charles W. Fry}
  {}
  {}

  \begin{SBVerse}
    I have found a friend in Jesus,

    He's ev'rything to me,

    He's the fairest of ten thousand to my soul;

    The ``Lily of the Valley,'' in Him alone I see,

    All I need to cleanse and make me fully whole.

    In sorrow He's my comfort, in trouble He's my stay,

    He tells me ev'ry care on Him to roll;

    He's the ``Lily of the Valley, the Bright and Morning Star,''

    He's the fairest of ten thousand to my soul.
  \end{SBVerse}

  \begin{SBVerse}
    He all my grief has taken, and all my sorrows borne,

    In temptation He's my strong and mighty tow'r;

    I have all for Him forsaken, and all my idols torn

    From my heart, and now He keeps me by His pow'r.

    Though all the world forsake me, and Satan tempt me sore,

    Through Jesus I shall safely reach the goal;

    He's the ``Lily of the Valley, the Bright and Morning Star,''

    He's the fairest of ten thousand to my soul.
  \end{SBVerse}

  \begin{SBVerse}
    He will never, never leave me, nor yet forsake me here,

    While I live by faith and do His blessed will;

    A wall of fire about me, I've nothing now to fear,

    With His manna He my hungry soul shall fill.

    Then sweeping up to glory, to see His blessed face,

    Where rivers of delight shall ever roll;

    He's the ``Lily of the Valley, the Bright and Morning Star,''

    He's the fairest of ten thousand to my soul.
  \end{SBVerse}
\end{song}

\WBPageBrk

\begin{song}{I've Wandered Far Away From God}{}
  {\SBPubDom}
  {William J. Kirkpatrick}
  {}
  {}

  \begin{SBVerse}
    I've wandered far away from God,

    Now I'm coming home;

    The paths of sin too long I've trod,

    Lord, I'm coming home.
  \end{SBVerse}

  \begin{SBOpGroup}
    Coming home, coming home,

    Nevermore to roam;

    Open wide Thine arms of love;

    Lord, I'm coming home.
  \end{SBOpGroup}

  \begin{SBVerse}
    I've wasted many precious years,

    Now I'm coming home;

    I now repent with bitter tears,

    Lord, I'm coming home.
  \end{SBVerse}

  \begin{SBVerse}
    I'm tired of sin and straying, Lord,

    Now I'm coming home;

    I'll trust Thy love, believe Thy word;

    Lord, I'm coming home.
  \end{SBVerse}

  \begin{SBVerse}
    My soul is sick, my heart is sore,

    Now I'm coming home;

    My strength renew, my hope restore:

    Lord, I'm coming home.
  \end{SBVerse}

  \begin{SBVerse}
    My only hope, my only plea,

    Now I'm coming home;

    That Jesus died, and died for me;

    Lord, I'm coming home.
  \end{SBVerse}

  \begin{SBVerse}
    I need His cleansing blood, I know,

    Now I'm coming home;

    O wash me whiter than the snow;

    Lord, I'm coming home.
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{Jesus, Keep Me Near The Cross}{}
  {\SBPubDom}
  {Fanny Crosby}
  {}
  {}

  \begin{SBVerse}
    Jesus, keep me near the cross,

    There a precious fountain;

    Free to all, a healing stream,

    Flows from Calv'ry's mountain.
  \end{SBVerse}

  \begin{SBOpGroup}
    In the cross, in the cross

    Be my glory ever,

    Till my ransomed soul shall find

    Rest beyond the river.
  \end{SBOpGroup}

  \begin{SBVerse}
    Near the cross, a trembling soul,

    Love and mercy found me;

    There the Bright and Morning Star

    Shed His beams around me.
  \end{SBVerse}

  \begin{SBVerse}
    Near the cross! O Lamb of God,

    Bring its scenes before me;

    Help me walk from day to day

    With its shadow o'er me.
  \end{SBVerse}

  \begin{SBVerse}
    Near the cross! I'll watch and wait,

    Hoping, trusting ever;

    Till I reach the golden strand,

    Just beyond the river.
  \end{SBVerse}
\end{song}

\begin{song}{Loved With Everlasting Love}{}
  {\SBPubDom}
  {George Wade Robinson}
  {}
  {}

  \begin{SBVerse}
    Loved with everlasting love,

    Led by grace that love to know;

    Spirit, breathing from above,

    Thou hast taught me it is so.

    Oh, this full and perfect peace!

    Oh, this transport all divine!

    In a love which cannot cease,

    I am His, and He is mine.
  \end{SBVerse}

  \begin{SBVerse}
    Heaven above is softer blue,

    Earth around is sweeter green;

    Something lives in every hue

    Christless eyes have never seen:

    Birds with gladder songs o'erflow,

    Flow'rs with deeper beauties shine,

    Since I know, as now I know,

    I am His, and He is mine.
  \end{SBVerse}

  \begin{SBVerse}
    Things that once were wild alarms

    Cannot now disturb my rest;

    Closed in everlasting arms,

    Pillowed on the loving breast.

    Oh, to lie forever here,

    Doubt and care and self resign,

    While He whispers in my ear,

    I am His, and He is mine.
  \end{SBVerse}

  \begin{SBVerse}
    His forever, only His:

    Who the Lord and me shall part?

    Ah, with what a rest of bliss

    Christ can fill the loving heart.

    Heaven and earth may fade and flee,

    Firstborn light in gloom decline;

    But, while God and I shall be,

    I am His, and He is mine.
  \end{SBVerse}
\end{song}

\begin{song}{My Faith Has Found A Resting Place}{}
  {\SBPubDom}
  {Lidie H. Edmunds}
  {}
  {}

  \begin{SBVerse}
    My faith has found a resting place,

    Not in device nor creed.

    I trust the ever-living One;

    His wounds for me shall plead.
  \end{SBVerse}

  \begin{SBOpGroup}
    I need no other argument,

    I need no other plea,

    It is enough that Jesus died,

    And that He died for me.
  \end{SBOpGroup}

  \begin{SBVerse}
    Enough for me that Jesus saves,

    This ends my fear and doubt;

    A sinful soul I come to Him,

    He'll never cast me out.
  \end{SBVerse}

  \begin{SBVerse}
    My heart is leaning on the Word,

    The written Word of God,

    Salvation by my Savior's name,

    Salvation thro' His blood.
  \end{SBVerse}

  \begin{SBVerse}
    My Great Physician heals the sick,

    The lost He came to save;

    For me His precious blood He shed,

    For me His life He gave.
  \end{SBVerse}
\end{song}

\begin{song}{Nearer, Still Nearer}{}
  {\SBPubDom}
  {Lelia N. Morris}
  {}
  {}

  \begin{SBVerse}
    Nearer, still nearer---close to Thy heart,

    Draw me, my Savior, so precious Thou art;

    Fold me, O fold me close to Thy breast;

    Shelter me safe in that Haven of Rest,

    Shelter me safe in that Haven of Rest.
  \end{SBVerse}

  \begin{SBVerse}
    Nearer, still nearer---nothing I bring,

    Naught as an off'ring to Jesus, my King---

    Only my sinful, now contrite heart;

    Grant me the cleansing Thy blood doth impart,

    Grant me the cleansing Thy blood doth impart.
  \end{SBVerse}

  \begin{SBVerse}
    Nearer, still nearer---Lord, to be Thine,

    Sin with its follies I gladly resign---

    All of its pleasures, pomp and its pride;

    Give me but Jesus, my Lord crucified,

    Give me but Jesus, my Lord crucified.
  \end{SBVerse}

  \begin{SBVerse}
    Nearer, still nearer---while life shall last,

    Till safe in glory my anchor is cast;

    Through endless ages, ever to be

    Nearer, my Savior, still nearer to Thee,

    Nearer, my Savior, still nearer to Thee.
  \end{SBVerse}
\end{song}

\WBPageBrk

\begin{song}{None But Christ Can Satisfy}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    O Christ, in Thee my soul hath found,

    And found in Thee alone,

    The peace, the joy I sought so long,

    The bliss till now unknown.
  \end{SBVerse}

  \begin{SBOpGroup}
    Now none but Christ can satisfy,

    None other name for me!

    There's love and life and lasting joy,

    Christ Jesus, found in Thee.
  \end{SBOpGroup}

  \begin{SBVerse}
    I sighed for rest and happiness,

    I yearned for them, not Thee;

    But while I passed my Saviour by,

    His love laid hold on me.
  \end{SBVerse}

  \begin{SBVerse}
    I tried the broken cisterns, ah!

    But how the waters failed;

    Even as I stooped to drink they fled,

    And mocked me as I wailed.
  \end{SBVerse}

  \begin{SBVerse}
    The pleasures lost I sadly mourned,

    But never wept for Thee,

    Till grace the sightless eyes received,

    Thy loveliness to see.
  \end{SBVerse}
\end{song}

\begin{song}{O, What A Saviour That He Died For Me}{}
  {\SBPubDom}
  {James McGranahan}
  {}
  {}

  \begin{SBVerse}
    Oh, what a Saviour that He died for me!

    From condemnation He hath made me free;

    ``He that believeth on the Son,'' said He,

    ``Hath everlasting life.''
  \end{SBVerse}

  \begin{SBOpGroup}
    ``Verily, verily, I say unto you;

    Verily, verily,'' message ever new!

    ``He that believeth on the Son,'' 'tis true!

    ``Hath everlasting life!''
  \end{SBOpGroup}

  \begin{SBVerse}
    All my iniquities on Him were laid,

    All my indebtedness by Him was paid;

    All who believe on Him, the Lord hath said,

    ``Hath everlasting life.''
  \end{SBVerse}

  \begin{SBVerse}
    Though poor and needy, I can trust my Lord;

    Though weak and sinful, I believe His Word;

    O glad message! Ev'ry child of God

    ``Hath everlasting life.''
  \end{SBVerse}

  \begin{SBVerse}
    Though all unworthy, yet I will not doubt;

    For him that cometh He will not cast out;

    ``He that believeth,'' oh, the good news shout!

    ``Hath everlasting life.''
  \end{SBVerse}
\end{song}

\begin{song}{I'm Depending On The Blood}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    On the golden streets of heaven all men hope to walk some day,

    Yet so many are not willing to accept the living way;

    But while others build on good works or opinions if they may,

    Hallelujah! hallelujah! I'm depending on the blood.
  \end{SBVerse}

  \begin{SBOpGroup}
    In the soul-cleansing blood of the Saviour,

    I've been wash'd in the crimson flood;

    Tho' the world may say

    There is hope some other way,

    I'm depending on the blood.
  \end{SBOpGroup}

  \begin{SBVerse}
    Some will tell us that God's mercy is their only hope and plea,

    That a soul He could not punish thro'out all eternity;

    But I read that my dear Saviour died for sinners just like me,

    Hallelujah! hallelujah! I'm depending on the blood.
  \end{SBVerse}

  \begin{SBVerse}
    As we look back thro' the ages where the kings and prophets trod,

    We may see their altars reeking with the sacrifice and blood;

    But those types were only pointing to the Paschal Lamb of God,

    Hallelujah! hallelujah! I'm depending on the blood.
  \end{SBVerse}

  \begin{SBVerse}
    'Tis the burden of that chorus over on the streets of light,

    That the blood from Calv'ry's mountain hath wash'd all their garments white;

    So I'll shout along life's pathway till I reach that land so bright,

    Hallelujah! hallelujah! I'm depending on the blood.
  \end{SBVerse}
\end{song}

\begin{song}{The Crowning Day Is Coming}{}
  {\SBPubDom}
  {El Nathan}
  {}
  {}

  \begin{SBVerse}
    Our Lord is now rejected,

    And by the world disowned,

    By the many still neglected,

    And by the few enthroned,

    But soon He'll come in glory,

    The hour is drawing nigh,

    For the crowning day is coming by and by.
  \end{SBVerse}

  \begin{SBOpGroup}
    Oh, the crowning day is coming,

    Is coming by and by,

    When our Lord shall come in ``power,''

    And ``glory'' from on high,

    Oh, the glorious night will gladden,

    Each waiting watchful eye,

    In the crowning day that's coming by and by.
  \end{SBOpGroup}

  \begin{SBVerse}
    The heav'ns shall glow with splendor,

    But brighter far than they

    The saints shall shine in glory,

    As Christ shall them array,

    The beauty of the Saviour,

    Shall dazzle ev'ry eye,

    In the crowning day that's coming by and by.
  \end{SBVerse}

  \begin{SBVerse}
    Our pain shall then be over,

    We'll sin and sigh no more,

    Behind us all of sorrow,

    And naught but joy before,

    A joy in our Redeemer,

    As we to Him are nigh,

    In the crowning day that's coming by and by.
  \end{SBVerse}

  \begin{SBVerse}
    Let all that look for, hasten

    The coming joyful day,

    By earnest consecration,

    To walk the narrow way,

    By gath'ring in the lost ones,

    For whom our Lord did die,

    For the crowning day that's coming by and by.
  \end{SBVerse}
\end{song}

\begin{song}{Shall We Gather At The River}{}
  {\SBPubDom}
  {Robert Lowry}
  {}
  {}

  \begin{SBVerse}
    Shall we gather at the river,

    Where bright angel feet have trod;

    With its crystal tide forever

    Flowing by the throne of God?
  \end{SBVerse}

  \begin{SBOpGroup}
    Yes, we'll gather at the river,

    The beautiful, the beautiful river;

    Gather with the saints at the river

    That flows by the throne of God.
  \end{SBOpGroup}

  \begin{SBVerse}
    On the margin of the river,

    Washing up its silver spray,

    We will walk and worship ever,

    All the happy golden day.
  \end{SBVerse}

  \begin{SBVerse}
    Ere we reach the shining river,

    Lay we ev'ry burden down;

    Grace our spirits will deliver,

    And provide a robe and crown.
  \end{SBVerse}

  \begin{SBVerse}
    Soon we'll reach the shining river,

    Soon our pilgrimage will cease;

    Soon our happy hearts will quiver

    With the melody of peace.
  \end{SBVerse}
\end{song}

\begin{song}{Standing On The Promises}{}
  {\SBPubDom}
  {Russell Kelso Carter}
  {}
  {}

  \begin{SBVerse}
    Standing on the promises of Christ, my King!

    Through eternal ages let His praises ring.

    ``Glory in the highest!'' I will shout and sing,

    Standing on the promises of God.
  \end{SBVerse}

  \begin{SBOpGroup}
    Standing, standing,

    Standing on the promises of God, my Savior;

    Standing, standing,

    I'm standing on the promises of God.
  \end{SBOpGroup}

  \begin{SBVerse}
    Standing on the promises that cannot fail!

    When the howling storms of doubt and fear assail,

    By the living Word of God I shall prevail,

    Standing on the promises of God.
  \end{SBVerse}

  \begin{SBVerse}
    Standing on the promises, I now can see

    Perfect, present cleansing in the blood for me;

    Standing in the liberty where Christ makes free,

    Standing on the promises of God.
  \end{SBVerse}

  \begin{SBVerse}
    Standing on the promises of Christ, the Lord,

    Bound to Him eternally by love's strong cord,

    Overcoming daily with the Spirit's Sword,

    Standing on the promises of God.
  \end{SBVerse}

  \begin{SBVerse}
    Standing on the promises I cannot fall,

    List'ning ev'ry moment to the Spirit's call,

    Resting in my Savior as my all in all,

    Standing on the promises of God.
  \end{SBVerse}
\end{song}

\begin{song}{Teach Me Thy Way, O Lord}{}
  {\SBPubDom}
  {B. Mansell Ramsey}
  {}
  {}

  \begin{SBVerse}
    Teach me Thy way, O Lord; teach me Thy way!

    Thy guiding grace afford; teach me Thy way!

    Help me to walk aright, more by faith, less by sight;

    Lead me with heav'nly light; teach me Thy way!
  \end{SBVerse}

  \begin{SBVerse}
    When I am sad at heart, teach me Thy way!

    When earthly joys depart, teach me Thy way!

    In hours of loneliness, in times of dire distress,

    In failure or success, teach me Thy way!
  \end{SBVerse}

  \begin{SBVerse}
    When doubts and fears arise, teach me Thy way!

    When storms o'erspread the skies, teach me Thy way!

    Shine thro' the cloud and rain, thro' sorrow, toil, and pain;

    Make Thou my pathway plain; teach me Thy way!
  \end{SBVerse}

  \begin{SBVerse}
    Long as my life shall last, teach me Thy way!

    Where'er my lot be cast, teach me Thy way!

    Until the race is run, until the journey's done,

    Until the crown is won, teach me Thy way!
  \end{SBVerse}
\end{song}

\begin{song}{Tell Me The Old, Old Story}{}
  {\SBPubDom}
  {A. Catherine Hankey}
  {}
  {}

  \begin{SBVerse}
    Tell me the old, old story,

    Of unseen things above,

    Of Jesus and His glory,

    Of Jesus and His love;

    Tell me the story simply,

    As to a little child,

    For I am weak and weary,

    And helpless and defiled.
  \end{SBVerse}

  \begin{SBOpGroup}
    Tell me the old, old story,

    Tell me the old, old story,

    Tell me the old, old story,

    Of Jesus and His love.
  \end{SBOpGroup}

  \begin{SBVerse}
    Tell me the story slowly,

    That I may take it in---

    That wonderful redemption,

    God's remedy for sin;

    Tell me the story often,

    For I forget so soon,

    The ``early dew'' of morning

    Has passed away at noon.
  \end{SBVerse}

  \begin{SBVerse}
    Tell me the story softly,

    With earnest tones and grave;

    Remember I'm the sinner

    Whom Jesus came to save;

    Tell me the story always,

    If you would really be,

    In any time of trouble,

    A comforter to me.
  \end{SBVerse}

  \begin{SBVerse}
    Tell me the same old story,

    When you have cause to fear

    That this world's empty glory

    Is costing me too dear;

    And when the Lord's bright glory

    Is dawning on my soul,

    Tell me the old, old story:

    ``Christ Jesus makes thee whole.''
  \end{SBVerse}
\end{song}

\begin{song}{What a day that will be}{}
  {\SBPubDom}
  {A. Catherine Hankey}
  {}
  {}

  \begin{SBVerse}

    There’s coming a day when no heartaches shall come

    No more clouds in the sky

    No more tears to dim the eye

    All is peace forever more

    On that happy golden shore

    What a day, glorious day that will be
  \end{SBVerse}
  \begin{SBOpGroup}
    What a day that will be when my Jesus I shall see

    When I look upon His face the one who saved my by His grace

    When He takes me by the hand and leads me to the promised land

    What a day, glorious day that will be

  \end{SBOpGroup}
  \begin{SBVerse}
    There will be no sorrows there

    And no more burdens to bear

    No more sickness and, no more pain

    No more parting over there

    And forever I will be with the one who died for me

    What a day, glorious day that will be
  \end{SBVerse}

\end{song}

\begin{song}{There Is No Love Like The Love Of Jesus}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    There is no love like the love of Jesus,

    Never to fade or fall,

    Till into the rest of the house of God

    He has gathered us all.
  \end{SBVerse}

  \begin{SBOpGroup}
    Jesus' love, precious love,

    Boundless, and pure, and free;

    Oh, turn to that love, weary wand'ring soul;

    Jesus pleadeth for thee.
  \end{SBOpGroup}

  \begin{SBVerse}
    There is no heart like the heart of Jesus,

    Filled with a tender love;

    No throb nor throe that our hearts can know;

    But He feels it above.
  \end{SBVerse}

  \begin{SBVerse}
    There is no eye like the eye of Jesus,

    Piercing so far away;

    Ne'er out of the sight of its tender light

    Can the wanderer stray.
  \end{SBVerse}

  \begin{SBVerse}
    There is no voice like the voice of Jesus,

    Tender and sweet its chime;

    Like musical ring of a flowing spring

    In the bright summertime.
  \end{SBVerse}

  \begin{SBVerse}
    Oh, let us hark to the voice of Jesus!

    Then we shall never roam;

    And we shall rest on His loving breast,

    And with Him we'll be one!
  \end{SBVerse}
\end{song}

\begin{song}{Close To Thee}{}
  {\SBPubDom}
  {Fanny Crosby}
  {}
  {}

  \begin{SBVerse}
    Thou my everlasting Portion,

    More than friend or life to me,

    All along my pilgrim journey,

    Savior, let me walk with Thee.
  \end{SBVerse}

  \begin{SBOpGroup}
    Close to Thee, close to Thee,

    Close to Thee, close to Thee;

    All along my pilgrim journey,

    Savior, let me walk with Thee.
  \end{SBOpGroup}

  \begin{SBVerse}
    Not for ease or worldly pleasure,

    Not for fame my prayer shall be;

    Gladly will I toil and suffer,

    Only let me walk with Thee.
  \end{SBVerse}

  \begin{SBOpGroup}
    Close to Thee, close to Thee,

    Close to Thee, close to Thee;

    Gladly will I toil and suffer,

    Only let me walk with Thee.
  \end{SBOpGroup}

  \begin{SBVerse}
    Lead me through the vale of shadows,

    Bear me o'er life's fitful sea;

    Then the gate of life eternal

    May I enter, Lord, with Thee.
  \end{SBVerse}

  \begin{SBOpGroup}
    Close to Thee, close to Thee,

    Close to Thee, close to Thee;

    Then the gate of life eternal

    May I enter, Lord, with Thee.
  \end{SBOpGroup}
\end{song}

\begin{song}{Trust And Obey}{}
  {\SBPubDom}
  {John H. Sammis}
  {}
  {}

  \begin{SBVerse}
    When we walk with the Lord

    In the light of His Word,

    What a glory He sheds on our way;

    While we do His good will,

    He abides with us still,

    And with all who will trust and obey.
  \end{SBVerse}

  \begin{SBOpGroup}
    Trust and obey,

    For there's no other way

    To be happy in Jesus,

    But to trust and obey.
  \end{SBOpGroup}

  \begin{SBVerse}
    Not a shadow can rise,

    Not a cloud in the skies,

    But His smile quickly drives it away;

    Not a doubt or a fear,

    Not a sigh or a tear,

    Can abide while we trust and obey.
  \end{SBVerse}

  \begin{SBVerse}
    Not a burden we bear,

    Not a sorrow we share,

    But our toil He doth richly repay;

    Not a grief or a loss,

    Not a frown or a cross,

    But is blest if we trust and obey.
  \end{SBVerse}

  \begin{SBVerse}
    But we never can prove

    The delights of His love,

    Until all on the altar we lay;

    For the favor He shows,

    And the joy He bestows,

    Are for them who will trust and obey.
  \end{SBVerse}

  \begin{SBVerse}
    Then in fellowship sweet

    We will sit at His feet,

    Or we'll walk by His side in the way;

    What He says we will do;

    Where He sends, we will go,

    Never fear, only trust and obey.
  \end{SBVerse}
\end{song}

\begin{song}{Where He May Lead Me I Will Go}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Where He may lead me I will go,

    For I have learned to trust Him so,

    And I remember 'twas for me,

    That He was slain on Calvary.
  \end{SBVerse}

  \begin{SBOpGroup}
    Jesus shall lead me night and day,

    Jesus shall lead me all the way,

    He is the truest Friend to me,

    For I remember Calvary.
  \end{SBOpGroup}

  \begin{SBVerse}
    O I delight in His command,

    Love to be led by His dear hand,

    His divine will is sweet to me,

    Hallowed by blood-stained Calvary.
  \end{SBVerse}

  \begin{SBVerse}
    Onward I go, nor doubt, nor fear,

    Happy with Christ, my Saviour near,

    Trusting that I some day shall see

    Jesus my Friend, of Calvary.
  \end{SBVerse}
\end{song}

\begin{song}{Give Me A Sight, O Savior}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Give me a sight, O Savior,

    Of Thy wondrous love to me,

    Of the love that brought Thee down to earth,

    To die on Calvary.
  \end{SBVerse}

  \begin{SBOpGroup}
    Oh, make me understand it,

    Help me to take it in,

    What it meant to Thee, the Holy One,

    To bear away my sin.
  \end{SBOpGroup}

  \begin{SBVerse}
    Was it the nails, O Savior,

    That bound Thee to the tree?

    Nay, 'twas Thine everlasting love,

    Thy love for me, for me.
  \end{SBVerse}

  \begin{SBVerse}
    Oh, wonder of all wonders,

    That through Thy death for me,

    My open sins, my secret sins,

    Can all forgiven be.
  \end{SBVerse}

  \begin{SBVerse}
    Then melt my heart, O Savior,

    Bend me, yea, break me down,

    Until I own Thee Conqueror,

    And Lord and Sov'reign crown.
  \end{SBVerse}
\end{song}

\begin{song}{They Nailed My Lord Upon The Tree}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    They nailed my Lord upon the tree

    And left Him, dying, there:

    Thro' love He suffered there for me;

    'Twas love beyond compare.
  \end{SBVerse}

  \begin{SBOpGroup}
    Crucified! Crucified!

    And nailed upon the tree!

    With pierc\`ed hands and feet and side!

    For you! For me!
  \end{SBOpGroup}

  \begin{SBVerse}
    Upon His head a crown of thorns,

    Upon His heart my shame;

    For me He prayed, for me He died,

    And, dying, spoke my name.
  \end{SBVerse}

  \begin{SBVerse}
    ``Forgive them, O forgive!'' He cried

    Then bowed His sacred head;

    ``O Lamb of God! my sacrifice!''

    For me Thy blood was shed.
  \end{SBVerse}

  \begin{SBVerse}
    His voice I hear, 'tis love I know;

    I worship at His feet;

    And kneeling there, at Calv'ry's cross,

    Redemption is complete.
  \end{SBVerse}
\end{song}

\begin{song}{On Calvary's Brow My Saviour Died}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    On Calvary's brow my Saviour died,

    'Twas there my Lord was crucified;

    'Twas on the cross He bled for me,

    And purchased there my pardon free.
  \end{SBVerse}

  \begin{SBOpGroup}
    O Calvary, dark Calvary,

    Where Jesus shed His blood for me.

    O Calvary, dark Calvary:

    Speak to my heart of Calvary.
  \end{SBOpGroup}

  \begin{SBVerse}
    'Mid rending rocks and darkening skies,

    My Saviour bows His head and dies;

    The opening veil reveals the way

    To Heaven's joys and endless day.
  \end{SBVerse}

  \begin{SBVerse}
    O Jesus, Lord, how can it be

    That Thou shouldst give Thy life for me,

    To bear the cross and agony

    In that dread hour on Calvary?
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{How Good Is The God We Adore}{}
  {\SBPubDom}
  {Joseph Hart}
  {}
  {}

  \begin{SBVerse}
    How good is the God we adore!

    Our faithful, unchangeable friend:

    His love is as great as His pow'r

    And knows neither measure nor end.
  \end{SBVerse}

  \begin{SBVerse}
    For Christ is the first and the last;

    His Spirit will guide us safe home;

    We'll praise Him for all that is past

    And trust Him for all that's to come.
  \end{SBVerse}
\end{song}

\begin{song}{Praise The Savior, Ye Who Know Him}{}
  {\SBPubDom}
  {Thomas Kelly}
  {}
  {}

  \begin{SBVerse}
    Praise the Savior, ye who know Him!

    Who can tell how much we owe Him?

    Gladly let us render to Him

    All we are and have.
  \end{SBVerse}

  \begin{SBVerse}
    Jesus is the name that charms us;

    He for conflicts fits and arms us;

    Nothing moves and nothing harms us

    When we trust in Him.
  \end{SBVerse}

  \begin{SBVerse}
    Trust in Him, ye saints, forever;

    He is faithful, changing never;

    Neither force nor guile can sever

    Those He loves from Him.
  \end{SBVerse}

  \begin{SBVerse}
    Keep us, Lord, oh, keep us cleaving

    To Thyself and still believing,

    Till the hour of Thy receiving

    The victorious Bride.
  \end{SBVerse}

  \begin{SBVerse}
    Then we shall be where we would be;

    Then we shall be what we should be;

    Things which are not now, nor could be,

    Then shall be our own.
  \end{SBVerse}
\end{song}

\begin{song}{I Stand Amazed In The Presence}{}
  {\SBPubDom}
  {Charles H. Gabriel}
  {}
  {}

  \begin{SBVerse}
    I stand amazed in the presence

    Of Jesus the Nazarene,

    And wonder how He could love me,

    A sinner condemned, unclean.
  \end{SBVerse}

  \begin{SBOpGroup}
    How marvelous! How wonderful!

    And my song shall ever be:

    How marvelous! How wonderful!

    Is my Savior's love for me!
  \end{SBOpGroup}

  \begin{SBVerse}
    For me it was in the garden,

    He prayed: ``Not my will, but Thine.''

    He had no tears for His own griefs,

    But sweat-drops of blood for mine.
  \end{SBVerse}

  \begin{SBVerse}
    In pity angels beheld Him,

    And came from the world of light

    To strengthen Him in the sorrows

    He bore for my soul that night.
  \end{SBVerse}

  \begin{SBVerse}
    He took my sins and my sorrows,

    He made them His very own;

    He bore the burden to Calv'ry,

    And suffered, and died alone.
  \end{SBVerse}

  \begin{SBVerse}
    When with the ransomed in glory

    His face I at last shall see,

    'Twill be my joy through the ages

    To sing of His love for me.
  \end{SBVerse}
\end{song}

\begin{song}{There's A Hill Lone And Gray}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    There's a hill lone and gray,

    In a land far away,

    In a country beyond the blue sea,

    Where beneath that fair sky,

    Went a man forth to die

    For the world and for you and for me.
  \end{SBVerse}

  \begin{SBOpGroup}
    Oh, it bows down my heart,

    And the tear-drops will start,

    When in mem'ry that gray hill I see;

    For 'twas there on its side

    Jesus suffered and died,

    To redeem a poor sinner like me.
  \end{SBOpGroup}

  \begin{SBVerse}
    Oh, so faint on the road,

    'Neath a world's heavy load,

    Comes a thorn-crowned Man on the way!

    With a cross He is bow'd,

    But still on thro' the crowd,

    He's ascending that hill lone and gray.
  \end{SBVerse}

  \begin{SBVerse}
    Hark! I hear the dull blow

    Of the hammer swung low;

    They are nailing my Lord to the tree!

    And the cross they up-raise,

    While the multitude gaze

    On the blest Lamb of dark Calvary!
  \end{SBVerse}

  \begin{SBVerse}
    How they mock Him in death

    To His last lab'ring breath,

    While His friends sadly weep o'er the way!

    But tho' lonely and faint

    Still no word of complaint

    Fell from Him on the hillock of gray.
  \end{SBVerse}

  \begin{SBVerse}
    Then the darkness came down,

    And the rocks rent around,

    And a cry pierc'd the sad-laden air!

    'Twas the voice of our King,

    Who received death's dark sting,

    All to save us from endless despair.
  \end{SBVerse}

  \begin{SBVerse}
    Let the sun hide its face,

    Let the earth reel apace,

    Over men who their Saviour have slain!

    But, behold! from the sod

    Comes the blest Lamb of God

    Who was slain, but is risen again.
  \end{SBVerse}

  \begin{SBOpGroup}
    Shout aloud, then, my soul,

    Let the glad tidings roll

    From the land to the ends of the sea!

    Jesus conquer'd the grave,

    And has risen to save

    The whole world, and to make us all free.
  \end{SBOpGroup}
\end{song}

\begin{song}{The Ninety And Nine}{}
  {\SBPubDom}
  {Elizabeth C. Clephane}
  {}
  {}

  \begin{SBVerse}
    There were ninety and nine that safely lay

    In the shelter of the fold

    But one was out on the hills away,

    Far off from the gates of gold---

    Away on the mountains wild and bare,

    Away from the tender Shepherd's care.
  \end{SBVerse}

  \begin{SBVerse}
    Lord, Thou hast here Thy ninety and nine.

    Are they not enough for Thee?

    But the Shepherd made answer: 'Tis of mine

    Has wandered away from me.

    And although the road be rough and steep,

    I go to the desert to find my sheep.
  \end{SBVerse}

  \begin{SBVerse}
    But none of the ransomed ever knew

    How deep were the waters crossed,

    Nor how dark was the night the Lord pass'd

    Ere He found His sheep that was lost.

    Out in the desert He heard its cry---

    Sick and helpless and ready to die.
  \end{SBVerse}

  \begin{SBVerse}
    ``Lord, what are these blood drops all the way

    That mark out the mountain's track?''

    ``They were shed for the one who'd gone astray

    Ere the Shepherd could bring him back.''

    ``Lord, why are these hands so rent and torn?''

    ``They're pierced tonight by many a thorn.''
  \end{SBVerse}

  \begin{SBVerse}
    But all thru' the mountains, thunder-riv'n,

    And up from the rocky steep,

    There rose such a cry to the gate of Heav'n,

    ``Rejoice, I have found my sheep!''

    And the angels echoed around the throne,

    ``Rejoice, for the Lord brings back His own!''
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{O Happy Day}{}
  {\SBPubDom}
  {Philip Doddridge}
  {}
  {}

  \begin{SBVerse}
    O happy day that fixed my choice

    On Thee, my Savior and my God!

    Well may this glowing heart rejoice,

    And tell its raptures all abroad.
  \end{SBVerse}

  \begin{SBOpGroup}
    Happy day, happy day,

    When Jesus washed my sins away!

    He taught me how to watch and pray,

    And live rejoicing every day;

    Happy day, happy day,

    When Jesus washed my sins away!
  \end{SBOpGroup}

  \begin{SBVerse}
    O happy bond, that seals my vows

    To Him who merits all my love!

    Let cheerful anthems fill His house,

    While to that sacred shrine I move.
  \end{SBVerse}

  \begin{SBVerse}
    'Tis done, the great transaction's done;

    I am my Lord's and He is mine;

    He drew me and I followed on,

    Rejoiced to own the call divine.
  \end{SBVerse}

  \begin{SBVerse}
    Now rest, my long-divided heart,

    Fixed on this blissful center, rest;

    Here have I found a nobler part,

    Here heavenly pleasures fill my breast.
  \end{SBVerse}

  \begin{SBVerse}
    High heaven that hears the solemn vow,

    That vow renewed shall daily hear;

    Till in life's latest hour I bow,

    And bless, in death, a bond so dear.
  \end{SBVerse}
\end{song}

\begin{song}{What A Friend We Have In Jesus}{}
  {\SBPubDom}
  {Joseph M. Scriven}
  {}
  {}

  \begin{SBVerse}
    What a friend we have in Jesus,

    All our sins and griefs to bear!

    What a privilege to carry

    Everything to God in prayer!

    O what peace we often forfeit,

    O what needless pain we bear,

    All because we do not carry

    Everything to God in prayer!
  \end{SBVerse}

  \begin{SBVerse}
    Have we trials and temptations?

    Is there trouble anywhere?

    We should never be discouraged;

    Take it to the Lord in prayer!

    Can we find a friend so faithful

    Who will all our sorrows share?

    Jesus knows our every weakness;

    Take it to the Lord in prayer!
  \end{SBVerse}

  \begin{SBVerse}
    Are we weak and heavy laden,

    Cumbered with a load of care?

    Precious Savior, still our refuge---

    Take it to the Lord in prayer!

    Do your friends despise, forsake you?

    Take it to the Lord in prayer!

    In His arms He'll take and shield you;

    You will find a solace there.
  \end{SBVerse}
\end{song}

\begin{song}{Christ Is Mine Forevermore}{}
  { CityAlight}
  {}
  {}
  {}
  \begin{SBVerse}
    Mine are days that God has numbered

    I was made to walk with Him

    Yet I look for worldly treasure

    And forsake the King of kings

    But mine is hope in my Redeemer

    Though I fall, His love is sure

    For Christ has paid for every failing

    I am His forevermore
  \end{SBVerse}
  \begin{SBVerse}
    Mine are tears in times of sorrow

    Darkness not yet understood

    Through the valley, I must travel

    Where I see no earthly good

    But mine is peace that flows from heaven

    And the strength in times of need

    I know my pain will not be wasted

    Christ completes His work in me
  \end{SBVerse}
  \begin{SBVerse}
    Mine are days here as a stranger

    Pilgrim on a narrow way

    One with Christ I will encounter

    Harm and hatred for His name

    But mine is armour for this battle

    Strong enough to last the war

    And He has said He will deliver

    Safely to the golden shore

    And mine are keys to Zion city

    Where beside the King I walk

    For there my heart has found its treasure

    Christ is mine forevermore
  \end{SBVerse}

  \begin{SBVerse}
    Come rejoice now, O my soul

    For His love is my reward

    Fear is gone and hope is sure

    Christ is mine forevermore!

    Come rejoice now, O my soul

    For His love is my reward

    Fear is gone and hope is sure

    Christ is mine forevermore!

    Come rejoice now, O my soul

    For His love is my reward

    Fear is gone and hope is sure

    Christ is mine forevermore!
  \end{SBVerse}
  \begin{SBVerse}
    And mine are keys to Zion city

    Where beside the King I walk

    For there my heart has found its treasure

    Christ is mine forevermore

    Christ is mine forevermore

    Christ is mine forevermore
  \end{SBVerse}

\end{song}

\begin{song}{Ancient Of Days}{}
  { CityAlight}
  {}
  {}
  {}
  \begin{SBVerse}
    Though the nations rage, kingdoms rise and fall

    There is still one King reigning over all

    So I will not fear, for this truth remains

    That my God is the Ancient of Days
  \end{SBVerse}
  \begin{SBOpGroup}
    None above Him, none before Him

    All of time in His hands

    For His throne, it shall remain and ever stand

    All the power, all the glory

    I will trust in His name

    For my God is the Ancient of Days
  \end{SBOpGroup}
  \begin{SBVerse}
    Though the dread of night overwhelms my soul

    He is here with me, I am not alone

    Oh, His love is sure, and He knows my name

    For my God is the Ancient of Days
  \end{SBVerse}
  \begin{SBVerse}
    Though I may not see what the future brings

    I will watch and wait for the Saviour King

    Then my joy complete, standing face to face

    In the presence of the Ancient of Days
  \end{SBVerse}
\end{song}

\begin{song}{I'd Rather Have Jesus}{}
  {\SBPubDom}
  {Rhea F. Miller}
  {}
  {}

  \begin{SBVerse}
    I'd rather have Jesus than silver or gold;

    I'd rather be His than have riches untold;

    I'd rather have Jesus than houses or lands.

    I'd rather be led by His nail-pierced hand.
  \end{SBVerse}

  \begin{SBOpGroup}
    Than to be the king of a vast domain

    Or be held in sin's dread sway.

    I'd rather have Jesus than anything

    This world affords today.
  \end{SBOpGroup}

  \begin{SBVerse}
    I'd rather have Jesus than men's applause;

    I'd rather be faithful to His dear cause;

    I'd rather have Jesus than world-wide fame.

    I'd rather be true to His holy name.
  \end{SBVerse}

  \begin{SBVerse}
    He's fairer than lilies of rarest bloom;

    He's sweeter than honey from out the comb;

    He's all that my hungering spirit needs.

    I'd rather have Jesus and let Him lead.
  \end{SBVerse}
\end{song}

\begin{song}{In God's Green Pastures}{}
  {}
  {Stuart Hamblen}
  {}
  {}

  \begin{SBVerse}
    In God’s green pastures feeding by His cool waters lie;

    Soft in the evening walk my Lord and I,

    All the sheep of His pasture

    Fare so wondrously fine; His sheep am I.
  \end{SBVerse}

  \begin{SBOpGroup}
    Waters cool (In the valley);

    Pastures green (on the mountain),

    In the evening (in the evening)

    Walk my Lord and I
  \end{SBOpGroup}

  \begin{SBOpGroup}
    Dark the night (in the valley),

    Rough the way (on the mountain),

    Step by step… (step by step).

    My Lord and I.
  \end{SBOpGroup}

  \begin{SBVerse}
    Through the streets of the city in the darkness of the night,

    Far from the fold, He heard my lonely cry.

    Now I sit at His table in the palace of light;

    His sheep am I.
  \end{SBVerse}
\end{song}

\begin{song}{O Listen To Our Wondrous Story}{}
  {\SBPubDom}
  {James M. Gray}
  {}
  {}

  \begin{SBVerse}
    O listen to our wondrous story,

    Counted once among the lost;

    Yet One came down from heaven's glory,

    Saving us at awful cost.
  \end{SBVerse}

  \begin{SBOpGroup}
    Who saved us from eternal loss? \textit{(Who but God's Son upon the cross?)}

    What did He do? \textit{(He died for you)}

    Where is He now? \textit{(Believe it thou)}

    In heaven interceding!
  \end{SBOpGroup}

  \begin{SBVerse}
    No angel could His place have taken,

    Highest of the high tho' he;

    The loved One on the cross forsaken

    Was One of the Godhead three!
  \end{SBVerse}

  \begin{SBVerse}
    Will you surrender to this Savior?

    To His scepter humbly bow;

    You, too, shall come to know His favor,

    He will save you, save you now.
  \end{SBVerse}
\end{song}

\begin{song}{You Are My All In All}{}
  {}
  {Dennis Jernigan}
  {}
  {}

  \begin{SBVerse}
    You are my strength when I am weak

    You are the treasure that I seek

    You are my all in all

    I'm seeking You like a precious jewel

    Lord, to give up I'd be a fool

    You are my all in all

  \end{SBVerse}

  \begin{SBOpGroup}
    Jesus, Lamb of God

    Holy is Your name

    Jesus, Lamb of God

    Holy is Your name

  \end{SBOpGroup}

  \begin{SBVerse}
    Taking my cross my sin my shame

    Raising again I praise Your name

    You are my all in all

    When I fall down You pick me up

    When I run dry You fill my cup

    You are my all in all
  \end{SBVerse}
\end{song}

\begin{song}{Seek Ye First}{}
  {}
  {Karen Lafferty}
  {}
  {}

  \begin{SBVerse}
    Seek ye first the kingdom of God

    And His righteousness;

    And all these things shall be added unto you.

    Hallelu, Hallelujah!
  \end{SBVerse}

  \begin{SBOpGroup}
    Hallelujah! Hallelujah!

    Hallelujah! Hallelu, hallelujah!
  \end{SBOpGroup}

  \begin{SBVerse}
    Ask, and it shall be given unto you;

    Seek, and you shall find.

    Knock, and it shall be opened unto you.

    Hallelu, Hallelujah!
  \end{SBVerse}

  \begin{SBVerse}
    Man shall not live by bread alone,

    But by every word

    That proceeds out from the mouth of God.

    Hallelu, Hallelujah!
  \end{SBVerse}
\end{song}

\begin{song}{Before The Throne Of God Above}{}
  {\SBPubDom}
  {Charitie Lees Bancroft}
  {}
  {}

  \begin{SBVerse}
    Before the throne of God above

    I have a strong and perfect plea:

    A great High Priest whose name is Love,

    Who ever lives and pleads for me.

    My name is graven on His hands,

    My name is written on His heart.

    I know that while in Heav'n He stands

    No tongue can bid me thence depart,

    No tongue can bid me thence depart.
  \end{SBVerse}

  \begin{SBVerse}
    When Satan tempts me to despair

    And tells me of the guilt within,

    Upward I look and see Him there,

    Who made an end of all my sin.

    Because the sinless Savior died,

    My sinful soul is counted free,

    For God the just is satisfied

    To look on Him and pardon me,

    To look on Him and pardon me.
  \end{SBVerse}

  \begin{SBVerse}
    Behold Him there, the risen Lamb,

    My perfect, spotless righteousness,

    The great unchangeable I AM,

    The King of glory and of grace.

    One with Himself I cannot die;

    My soul is purchased by His blood.

    My life is hid with Christ on high,

    With Christ, my Savior and my God,

    With Christ, my Savior and my God.
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{The Way Of The Cross Leads Home}{}
  {\SBPubDom}
  {Jessie Brown Pounds}
  {}
  {}

  \begin{SBVerse}
    I must needs go home by the way of the cross;

    There's no other way but this.

    I shall ne'er get sight of the Gates of Light

    If the way of the cross I miss.
  \end{SBVerse}

  \begin{SBOpGroup}
    The way of the cross leads home.

    The way of the cross leads home.

    It is sweet to know, as I onward go,

    The way of the cross leads home.
  \end{SBOpGroup}

  \begin{SBVerse}
    I must needs go home in the blood-sprinkled way,

    The path that the Savior trod,

    If I ever climb to the heights sublime,

    Where the soul is at home with God.
  \end{SBVerse}

  \begin{SBVerse}
    Then I bid farewell to the way of the world,

    To walk in it nevermore;

    For the Lord says, ``Come,'' and I seek my home

    Where He waits at the open door.
  \end{SBVerse}
\end{song}

\begin{song}{O How Happy Are They}{}
  {\SBPubDom}
  {Charles Wesley}
  {}
  {}

  \begin{SBVerse}
    O how happy are they who the Saviour obey,

    And have laid up their treasure above.

    Tongue can never express the sweet comfort and peace

    Of a soul filled with Jesus' love.
  \end{SBVerse}

  \begin{SBOpGroup}
    We'll all shout hallelujah

    As we march along the way.

    We will sing redeeming love

    With the shining host above,

    And with Jesus we'll be happy all the day.
  \end{SBOpGroup}

  \begin{SBVerse}
    That sweet comfort is mine now the favour divine

    I've received through the blood of the Lamb;

    With my heart I believe, and what joy I receive,

    What a Heaven in Jesus' name!
  \end{SBVerse}

  \begin{SBVerse}
    'Tis a Heaven below my Redeemer to know,

    And the angels can do nothing more

    Than to fall at His feet and the story repeat,

    And the lover of sinners adore.
  \end{SBVerse}

  \begin{SBVerse}
    O the rapturous height of the holy delight

    Which I feel in the life-giving blood!

    Of my Saviour possessed, I am perfectly bless\`ed,

    As if filled with the Heaven of God.
  \end{SBVerse}
\end{song}

\begin{song}{Lord Jesus! My Savior! How Vast Thy Love To Me}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Lord Jesus! my Savior! how vast Thy love to me;

    I'll bathe in its full ocean to all eternity,

    And wending on to glory this all my song shall be:

    ``I was a guilty sinner, but Jesus died for me.''
  \end{SBVerse}

  \begin{SBVerse}
    O Calv'ry! O Calv'ry; the thorn-crown and the spear

    There doth Thy love, Lord Jesus, in bleeding wounds appear;

    Oh, depths of grace and mercy, to those dear wounds I flee;

    ``I was a guilty sinner, but Jesus died for me.''
  \end{SBVerse}

  \begin{SBVerse}
    Adore Him, adore Him, the glorious work is done;

    And now He'll not condemn me, 'twas laid upon His Son;

    'Tis finished cried the Savior, and I my title see;

    ``I was a guilty sinner, but Jesus died for me.''
  \end{SBVerse}

  \begin{SBVerse}
    In glory, in glory, ``forever with the Lord,''

    I'll tune my harp with others, and sing with sweet accord;

    And as we praise together, this all my song shall be:

    ``I was a guilty sinner, but Jesus died for me.''
  \end{SBVerse}
\end{song}

\begin{song}{Look, Ye Saints, The Sight Is Glorious}{}
  {\SBPubDom}
  {Thomas Kelly}
  {}
  {}

  \begin{SBVerse}
    Look, ye saints, the sight is glorious:

    See the Man of Sorrows now;

    From the fight returned victorious,

    Every knee to Him shall bow.

    Crown Him! Crown Him!

    Crowns become the Victor's brow.
  \end{SBVerse}

  \begin{SBVerse}
    Crown the Savior, angels, crown Him;

    Rich the trophies Jesus brings;

    In the seat of pow'r enthrone Him,

    While the vault of heaven rings.

    Crown Him! Crown Him!

    Crown the Savior King of kings.
  \end{SBVerse}

  \begin{SBVerse}
    Sinners in derision crowned Him,

    Mocking thus the Savior's claim;

    Saints and angels crowd around Him,

    Own His title, praise His name.

    Crown Him! Crown Him!

    Spread abroad the Victor's fame!
  \end{SBVerse}

  \begin{SBVerse}
    Hark, those bursts of acclamation!

    Hark! those loud triumphant chords!

    Jesus takes the highest station;

    O what joy the sight affords!

    Crown Him! Crown Him!

    King of kings, and Lord of lords!
  \end{SBVerse}
\end{song}

\begin{song}{How Deep The Father's Love For Us}{}
  { Stuart Townend}
  {Stuart Townend}
  {}
  {}

  \begin{SBVerse}
    How deep the Father's love for us,

    How vast beyond all measure,

    That He should give His only Son

    To make a wretch His treasure.

    How great the pain of searing loss -

    The Father turns His face away,

    As wounds which mar the Chosen One

    Bring many sons to glory.
  \end{SBVerse}

  \begin{SBVerse}
    Behold the man upon a cross,

    My sin upon His shoulders;

    Ashamed, I hear my mocking voice

    Call out among the scoffers.

    It was my sin that held Him there

    Until it was accomplished;

    His dying breath has brought me life -

    I know that it is finished.
  \end{SBVerse}

  \begin{SBVerse}
    I will not boast in anything,

    No gifts, no power, no wisdom;

    But I will boast in Jesus Christ,

    His death and resurrection.

    Why should I gain from His reward?

    I cannot give an answer;

    But this I know with all my heart -

    His wounds have paid my ransom.
  \end{SBVerse}
\end{song}

\begin{song}{The Sands Of Time Are Sinking}{}
  {\SBPubDom}
  {Anne Ross Cousin}
  {}
  {}

  \begin{SBVerse}
    The sands of time are sinking,

    The dawn of heaven breaks,

    The summer morn I've sighed for,

    The fair, sweet morn awakes:

    Dark, dark hath been the midnight,

    But dayspring is at hand,

    And glory, glory dwelleth

    In Emmanuel's land.
  \end{SBVerse}

  \begin{SBVerse}
    Oh! Christ He is the fountain,

    The deep sweet well of love!

    The streams on earth I've tasted,

    More deep I'll drink above:

    There, to an ocean fullness,

    His mercy doth expand,

    And glory, glory dwelleth

    In Emmanuel's land.
  \end{SBVerse}

  \begin{SBVerse}
    I've wrestled on towards heaven,

    'Gainst storm, and wind, and tide,

    Now like a weary traveller

    That leaneth on his guide,

    Amid the shades of evening,

    While sinks life's lingering sand,

    I hail the glory dawning

    From Immanuel's land.
  \end{SBVerse}

  \begin{SBVerse}
    The bride eyes not her garment,

    But her dear Bridegroom's face;

    I will not gaze at glory,

    But on my King of Grace---

    Not at the crown He giveth,

    But on His pierced hand;

    The Lamb is all the glory

    Of Emmanuel's land.
  \end{SBVerse}

  \begin{SBVerse}
    Oh! I am my Beloved's,

    And my Beloved's mine!

    He brings a poor vile sinner

    Into His ``house of wine;''

    I stand upon His merit,

    I know no other stand,

    Not e'en where glory dwelleth

    In Emmanuel's land.
  \end{SBVerse}
\end{song}

\begin{song}{I Owe It All To Thee}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Lord, when I think upon the love

    Which Thou to me hast shown,

    To die upon the cross, that Thou

    May'st claim me for Thine own.

    I cannot tell why Thou didst show

    Such love to one like me,

    Save that it is, that I might know

    I owe it all to Thee.
  \end{SBVerse}

  \begin{SBVerse}
    There is no goodness in myself,

    To win such precious love;

    I loved Thee not---Thou lovedst me,

    And called me from above:

    I heard Thy voice, it won my heart,

    And bade my doubtings flee;

    It gave me rest and peace---oh, yes,

    I owe it all to Thee.
  \end{SBVerse}

  \begin{SBVerse}
    And still upheld by power divine,

    I urge my way along

    In haste to reach the promised rest,

    The bright, glad home of song,

    And then when glory on me bursts,

    And I Thy glory see,

    Again I'll raise the happy song,

    ``I owe it all to Thee.''
  \end{SBVerse}
\end{song}

\begin{song}{When The Roll Is Called Up Yonder}{}
  {\SBPubDom}
  {James M. Black}
  {}
  {}

  \begin{SBVerse}
    When the trumpet of the Lord shall sound and time shall be no more,

    And the morning breaks, eternal, bright and fair;

    When the saved of earth shall gather over on the other shore,

    And the roll is called up yonder, I'll be there.
  \end{SBVerse}

  \begin{SBOpGroup}
    When the roll is called up yonder,

    When the roll is called up yonder,

    When the roll is called up yonder,

    When the roll is called up yonder, I'll be there.
  \end{SBOpGroup}

  \begin{SBVerse}
    On that bright and cloudless morning when the dead in Christ shall rise,

    And the glory of His resurrection share;

    When His chosen ones shall gather to their home beyond the skies,

    And the roll is called up yonder, I'll be there.
  \end{SBVerse}

  \begin{SBVerse}
    Let us labor for the Master from the dawn till setting sun;

    Let us talk of all His wondrous love and care.

    Then when all of life is over and our work on earth is done,

    And the roll is called up yonder, I'll be there.
  \end{SBVerse}
\end{song}

\begin{song}{Because He Lives}{}
  { Gaither}
  {Bill and Gloria Gaither}
  {}
  {}

  \begin{SBVerse}
    God sent His son,

    They called Him, Jesus;

    He came to love,

    Heal and forgive;

    He lived and died

    To buy my pardon,

    An empty grave is there

    To prove my Savior lives!
  \end{SBVerse}

  \begin{SBOpGroup}
    Because He lives,

    I can face tomorrow!

    Because He lives,

    All fear is gone.

    Because I know

    He holds the future,

    And life is worth the living,

    Just because He lives!
  \end{SBOpGroup}

  \begin{SBVerse}
    How sweet to hold

    A newborn baby,

    And feel the pride

    And joy he brings;

    But greater still

    The calm assurance:

    This child can face

    Uncertain days because He Lives!
  \end{SBVerse}

  \begin{SBVerse}
    And then one day,

    I'll cross the river,

    I'll fight life's final

    War with pain;

    And then, as death

    Gives way to victory,

    I'll see the lights of glory

    And I'll know He lives!
  \end{SBVerse}
\end{song}

\begin{song}{As The Deer}{}
  {}
  {Martin Nystrom}
  {}
  {}

  \begin{SBVerse}
    As the deer pants for the water

    So my soul longs after You

    You alone are my heart's desire

    And I long to worship You
  \end{SBVerse}

  \begin{SBOpGroup}
    You alone are my strength, my shield

    To You alone may my spirit yield

    You alone are my heart's desire

    And I long to worship You
  \end{SBOpGroup}

  \begin{SBVerse}
    I want You more than gold or silver

    Only You can satisfy

    You alone are the real joy giver

    And the apple of my eye
  \end{SBVerse}

  \begin{SBVerse}
    You're my friend and You're my brother

    Even though you are a King

    I love You more than any other

    So much more than anything
  \end{SBVerse}
\end{song}

\begin{song}{Turn Your Eyes Upon Jesus}{}
  {\SBPubDom}
  {Helen H. Lemmel}
  {}
  {}

  \begin{SBVerse}
    O soul, are you weary and troubled?

    No light in the darkness you see?

    There's light for a look at the Savior,

    And life more abundant and free!
  \end{SBVerse}

  \begin{SBOpGroup}
    Turn your eyes upon Jesus,

    Look full in His wonderful face,

    And the things of earth will grow strangely dim,

    In the light of His glory and grace.
  \end{SBOpGroup}

  \begin{SBVerse}
    Thro' death into life everlasting,

    He passed, and we follow Him there;

    O'er us sin no more hath dominion---

    For more than conqu'rors we are!
  \end{SBVerse}

  \begin{SBVerse}
    His Word shall not fail you---He promised;

    Believe Him, and all will be well:

    Then go to a world that is dying,

    His perfect salvation to tell!
  \end{SBVerse}
\end{song}

\begin{song}{It Is Well With My Soul}{}
  {\SBPubDom}
  {Horatio G. Spafford}
  {}
  {}

  \begin{SBVerse}
    When peace like a river attendeth my way,

    When sorrows like sea billows roll;

    Whatever my lot, Thou hast taught me to say,

    ``It is well, it is well with my soul.''
  \end{SBVerse}

  \begin{SBOpGroup}
    It is well with my soul;

    It is well, it is well with my soul.
  \end{SBOpGroup}

  \begin{SBVerse}
    Though Satan should buffet, though trials should come,

    Let this blest assurance control:

    That Christ has regarded my helpless estate,

    And has shed His own blood for my soul.
  \end{SBVerse}

  \begin{SBVerse}
    My sin---oh, the bliss of this glorious thought!---

    My sin, not in part, but the whole,

    Is nailed to the cross, and I bear it no more;

    Praise the Lord, praise the Lord, O my soul!
  \end{SBVerse}

  \begin{SBVerse}
    O Lord, haste the day when my faith shall be sight,

    The clouds be rolled back as a scroll;

    The trump shall resound and the Lord shall descend;

    Even so, it is well with my soul.
  \end{SBVerse}
\end{song}

\begin{song}{In Christ Alone}{}
  {}
  {Keith Getty and Stuart Townend}
  {}
  {}

  \begin{SBVerse}
    In Christ alone my hope is found;

    He is my light, my strength, my song;

    this Cornerstone, this solid ground,

    firm through the fiercest drought and storm.

    What heights of love, what depths of peace

    when fears are stilled, when strivings cease;

    my Comforter, my All in All;

    here in the love of Christ I stand.
  \end{SBVerse}

  \begin{SBVerse}
    In Christ alone who took on flesh;

    fullness of God in helpless babe.

    This gift of love and righteousness

    scorned by the ones He came to save;

    'til on that cross as Jesus died

    the wrath of God was satisfied;

    for ev'ry sin on Him was laid;

    here in the death of Christ I live.
  \end{SBVerse}

  \begin{SBVerse}
    There in the ground His body lay;

    Light of the world by darkness slain.

    Then bursting forth in glorious day,

    up from the grave He rose again!

    And as He stands in victory,

    sin's curse has lost its grip on me;

    for I am His and He is mine,

    bought with the precious blood of Christ!
  \end{SBVerse}

  \begin{SBVerse}
    No guilt in life, no fear in death;

    this is the pow'r of Christ in me.

    From life's first cry to final breath,

    Jesus commands my destiny.

    No pow'r of hell, no scheme of man

    can ever pluck me from His hand;

    'til He returns or calls me home,

    here in the pow'r of Christ I'll stand!
  \end{SBVerse}
\end{song}

\begin{song}{I Know Who Holds Tomorrow}{}
  {}
  {Ira Stanphill}
  {}
  {}

  \begin{SBVerse}
    I don't know about tomorrow,

    I just live from day to day.

    I don't borrow from its sunshine,

    For its skies may turn to gray.

    I don't worry o'er the future,

    For I know what Jesus said,

    And today I'll walk beside Him,

    For He knows what is ahead.
  \end{SBVerse}

  \begin{SBOpGroup}
    Many things about tomorrow,

    I don't seem to understand;

    But I know who holds tomorrow,

    And I know who holds my hand.
  \end{SBOpGroup}

  \begin{SBVerse}
    Every step is getting brighter,

    As the golden stairs I climb;

    Every burden's getting lighter;

    Every cloud is silver lined.

    There the sun is always shining,

    There no tear will dim the eye,

    At the ending of the rainbow,

    Where the mountains touch the sky.
  \end{SBVerse}

  \begin{SBVerse}
    I don't know about tomorrow,

    It may bring me poverty;

    But the one who feeds the sparrow,

    Is the one who stands by me.

    And the path that be my portion,

    May be through the flame or flood,

    But His presence goes before me,

    And I'm covered with His blood.
  \end{SBVerse}
\end{song}

\begin{song}{If That Isn't Love}{}
  {}
  {Dottie Rambo}
  {}
  {}

  \begin{SBVerse}
    He left the splendor of heaven

    Knowing His destiny

    Was the lonely hill of Golgotha

    There to lay down His life for me
  \end{SBVerse}

  \begin{SBOpGroup}
    And if that isn't love

    Then the ocean is dry

    There's no stars in the sky

    And the little sparrows can't fly

    Yeah if that isn't love

    Then heaven's a myth

    There's no feeling like this

    If that isn't love
  \end{SBOpGroup}

  \begin{SBVerse}
    Even in death He remembered

    The thief hanging by His side

    Then he spoke of love and compassion

    And He took him to paradise
  \end{SBVerse}
\end{song}

\begin{song}{Pass It On}{}
  {}
  {Kurt Kaiser}
  {}
  {}

  \begin{SBVerse}
    It only takes a spark

    To get a fire going

    And soon all those around

    Can warm up in its glowing

    That's how it is with God's love

    Once you've experienced it

    You spread His love to ev'ryone

    You want to pass it on

  \end{SBVerse}

  \begin{SBVerse}
    What a wondrous time is spring

    When all the trees are budding

    The birds begin to sing

    The flowers start their blooming

    That's how it is with God's love

    Once you've experienced it

    You want to sing it's fresh like spring

    You want to pass it on

  \end{SBVerse}

  \begin{SBVerse}
    I wish for you my friend

    This happiness that I've found

    You can depend on Him

    It matters not where you're bound

    I'll shout it from the mountain top

    I want my world to know

    The Lord of love has come to me

    I want to pass it on
  \end{SBVerse}
\end{song}

\begin{song}{Here Is Love, Vast As The Ocean}{}
  {\SBPubDom}
  {William Rees}
  {}
  {}

  \begin{SBVerse}
    Here is love, vast as the ocean,

    Loving-kindness as the flood;

    When the Prince of Life, my ransom,

    Shed for me His precious blood.

    Who His love will not remember?

    Who can cease to sing His praise?

    He shall never be forgotten,

    Through Heav'n's everlasting days.
  \end{SBVerse}

  \begin{SBVerse}
    On the mount of crucifixion,

    Fountains opened deep and wide,

    Through the flood-gates of God's mercy,

    Flowed the vast and gracious tide;

    Grace and love, like mighty rivers

    Poured incessant from above,

    And God's peace and perfect justice

    Kissed a guilty world in love.
  \end{SBVerse}

  \begin{SBVerse}
    Let me all Your love accepting,

    Love You, ever all my days;

    Let me seek Your kingdom only

    And my life be to Your praise;

    You alone will be my glory,

    Nothing in the world I see;

    You have cleansed and sanctified me,

    You have loved and set me free.
  \end{SBVerse}

  \begin{SBVerse}
    In Your truth You will direct me

    By Your Spirit, thru' Your Word;

    And Your grace my need is meeting,

    As I trust in You, my Lord.

    All Your fulness You are pouring

    From Your endless wells above,

    Without measure, full and boundless

    As I yield myself in love.
  \end{SBVerse}
\end{song}

\begin{song}{My Redeemer}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    My Redeemer, oh what beauties

    In that lovely name appear;

    None but Jesus in His glories

    Shall the honored title wear.

    My Redeemer, my Redeemer,

    Thou hast my salvation wrought.
  \end{SBVerse}

  \begin{SBVerse}
    Sunk in ruin, sin, and misery,

    Bound by Satan's captive chain,

    Guided by his artful treachery,

    Hurrying on to endless pain:

    My Redeemer, my Redeemer,

    Plucked me as a brand from hell.
  \end{SBVerse}

  \begin{SBVerse}
    Mine by covenant, mine forever,

    Mine by oath, and mine by blood,

    Mine---nor time the bond shall sever,

    Mine as an unchanging God:

    My Redeemer, my Redeemer,

    Oh, how sweet to call Thee mine!
  \end{SBVerse}

  \begin{SBVerse}
    When in heaven I see Thy glory,

    When before Thy throne I bow,

    Perfected I shall be like Thee,

    Fully Thy redemption know.

    My Redeemer, my Redeemer,

    Then shall hear me shout His praise.
  \end{SBVerse}
\end{song}

\begin{song}{Channels Only}{}
  {\SBPubDom}
  {Mary E. Maxwell}
  {}
  {}

  \begin{SBVerse}
    How I praise Thee, precious Savior,

    That Thy love laid hold of me;

    Thou hast saved and cleansed and filled me

    That I might Thy channel be.
  \end{SBVerse}

  \begin{SBOpGroup}
    Channels only, blessed Master,

    But with all Thy wondrous pow'r

    Flowing through us, Thou canst use us

    Every day and every hour.
  \end{SBOpGroup}

  \begin{SBVerse}
    Just a channel full of blessing,

    To the thirsty hearts around;

    To tell out Thy full salvation,

    All Thy loving message sound.
  \end{SBVerse}

  \begin{SBVerse}
    Emptied that Thou shouldest fill me,

    A clean vessel in Thy hand;

    With no pow'r but as Thou givest

    Graciously with each command.
  \end{SBVerse}

  \begin{SBVerse}
    Witnessing Thy pow'r to save me,

    Setting free from self and sin;

    Thou who boughtest to possess me,

    In Thy fullness, Lord, come in.
  \end{SBVerse}

  \begin{SBVerse}
    Jesus, fill now with Thy Spirit

    Hearts that full surrender know;

    That the streams of living water

    From our inner self may flow.
  \end{SBVerse}
\end{song}

\begin{song}{I Have Been At The Altar}{}
  {\SBPubDom}
  {Amelia Matilda Hull}
  {}
  {}

  \begin{SBVerse}
    I have been at the altar and witnessed the Lamb

    Burnt wholly to ashes for me;

    And watched its sweet savour ascending on high,

    Accepted, O Father, by Thee.
  \end{SBVerse}

  \begin{SBVerse}
    And lo, while I gazed at the glorious sight,

    A voice from above reached mine ears;

    ``By this thine iniquity's taken away,

    And no trace of it on thee appears.''
  \end{SBVerse}

  \begin{SBVerse}
    ``An end of thy sin has been made for thee here

    By Him who its penalty bore;

    With blood it is blotted eternally out,

    And I will not remember it more.''
  \end{SBVerse}

  \begin{SBVerse}
    O Lord, I believe it with wonder and joy;

    Confirm, Thou, this precious belief;

    While daily I learn that I am, in myself,

    Of sinners the vilest and chief.
  \end{SBVerse}
\end{song}

\begin{song}{And Is It So! I Shall Be Like Thy Son?}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    And is it so! I shall be like Thy Son?

    Is this the grace which He for me has won?

    Father of glory---thought beyond all thought!

    In glory, to His own blest likeness brought!
  \end{SBVerse}

  \begin{SBVerse}
    Oh, Jesus, Lord, who loved me like to Thee?

    Fruit of Thy work, with Thee, too, there to see

    Thy glory, Lord, while endless ages roll,

    Myself the prize and travail of Thy soul.
  \end{SBVerse}

  \begin{SBVerse}
    Yet it must be: Thy love had not its rest

    Were Thy redeemed not with Thee fully blest;

    That love that gives not as the world, but shares

    All it possesses with its loved co-heirs.
  \end{SBVerse}

  \begin{SBVerse}
    Nor I alone; Thy loved ones, all complete

    In glory, round Thee there with joy shall meet

    All like Thee, for Thy glory like Thee, Lord,

    Object supreme of all, by all adored.
  \end{SBVerse}
\end{song}

\begin{song}{Face To Face With Christ My Savior}{}
  {\SBPubDom}
  {Carrie E. Breck}
  {}
  {}

  \begin{SBVerse}
    Face to face with Christ, my Savior,

    Face to face, what will it be?

    When with rapture I behold Him,

    Jesus Christ who died for me.
  \end{SBVerse}

  \begin{SBOpGroup}
    Face to face shall I behold Him,

    Far beyond the starry sky;

    Face to face in all His glory,

    I shall see Him by and by.
  \end{SBOpGroup}

  \begin{SBVerse}
    Only faintly now I see Him,

    With the darkened veil between;

    But a blessed day is coming,

    When His glory shall be seen.
  \end{SBVerse}

  \begin{SBVerse}
    Face to face, oh, blissful moment!

    Face to face, to see and know;

    Face to face with my Redeemer,

    Jesus Christ who loved me so.
  \end{SBVerse}
\end{song}

\begin{song}{I Will Sing Of My Redeemer}{}
  {\SBPubDom}
  {Philip P. Bliss}
  {}
  {}

  \begin{SBVerse}
    I will sing of my Redeemer

    And His wondrous love to me;

    On the cruel cross He suffered,

    From the curse to set me free.
  \end{SBVerse}

  \begin{SBOpGroup}
    Sing, O sing of my Redeemer!

    With His blood He purchased me;

    On the cross He sealed my pardon,

    Paid the debt, and made me free.
  \end{SBOpGroup}

  \begin{SBVerse}
    I will tell the wondrous story,

    How my lost estate to save,

    In His boundless love and mercy,

    He the ransom freely gave.

    I will praise my dear Redeemer,

    His triumphant power I'll tell:

    How the victory He gives me

    Over sin and death and hell.
  \end{SBVerse}

  \begin{SBVerse}
    I will sing of my Redeemer

    And His heavenly love for me;

    He from death to life has brought me,

    Son of God, with Him to be.
  \end{SBVerse}
\end{song}

\begin{song}{I Know Whom I Have Believed}{}
  {\SBPubDom}
  {Daniel W. Whittle}
  {}
  {}

  \begin{SBVerse}
    I know not why God's wondrous grace

    To me He hath made known,

    Nor why, unworthy, Christ in love

    Redeemed me for His own.
  \end{SBVerse}

  \begin{SBOpGroup}
    But I know Whom I have believ\`ed,

    And am persuaded that He is able

    To keep that which I've committed

    Unto Him against that day.
  \end{SBOpGroup}

  \begin{SBVerse}
    I know not how this saving faith

    To me He did impart,

    Nor how believing in His Word

    Wrought peace within my heart.
  \end{SBVerse}

  \begin{SBVerse}
    I know not how the Spirit moves,

    Convincing men of sin,

    Revealing Jesus through the Word,

    Creating faith in Him.
  \end{SBVerse}

  \begin{SBVerse}
    I know not what of good or ill

    May be reserved for me,

    Of weary ways or golden days,

    Before His face I see.
  \end{SBVerse}

  \begin{SBVerse}
    I know not when my Lord may come,

    At night or noonday fair,

    Nor if I'll walk the vale with Him,

    Or meet Him in the air.
  \end{SBVerse}
\end{song}

\begin{song}{Lord Jesus, Thou Who Only Art}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Lord Jesus, Thou who only art

    The endless source of purest joy,

    O come and fill this longing heart;

    May nought but Thee my thoughts employ.

    Teach me on Thee to fix my eye,

    For none but Thee can satisfy.
  \end{SBVerse}

  \begin{SBVerse}
    The joys of earth can never fill

    The heart that's tasted of Thy love;

    No portion would I seek until

    I reign with Thee, my Lord, above,

    When I shall gaze upon Thy face,

    And know more fully all Thy grace.
  \end{SBVerse}

  \begin{SBVerse}
    When from Thy radiant throne on high

    Thou didst my fall and ruin see,

    Thou cam'st on earth for me to die,

    That I might share that throne with Thee.

    Loved with an everlasting love,

    My hopes, my joys are all above.
  \end{SBVerse}

  \begin{SBVerse}
    O what is all that earth can give?

    I'm called to share in God's own joy;

    Dead to the world, in Thee I live,

    In Thee I've bliss without alloy:

    Well may I earthly joys resign;

    All things are mine, and I am Thine!
  \end{SBVerse}

  \begin{SBVerse}
    Till Thou shalt come to take me home,

    Be this my one ambition, Lord,

    Self, sin, the world, to overcome,

    Fast clinging to Thy faithful Word;

    More of Thyself each day to know,

    And more into Thine image grow.
  \end{SBVerse}
\end{song}

\begin{song}{When We All Get To Heaven}{}
  {\SBPubDom}
  {Eliza E. Hewitt}
  {}
  {}

  \begin{SBVerse}
    Sing the wondrous love of Jesus,

    Sing His mercy and His grace;

    In the mansions bright and blessed

    He'll prepare for us a place.
  \end{SBVerse}

  \begin{SBOpGroup}
    When we all get to heaven,

    What a day of rejoicing that will be!

    When we all see Jesus,

    We'll sing and shout the victory!
  \end{SBOpGroup}

  \begin{SBVerse}
    While we walk the pilgrim pathway

    Clouds will overspread the sky;

    But when trav'ling days are over

    Not a shadow, not a sigh.
  \end{SBVerse}

  \begin{SBVerse}
    Let us then be true and faithful,

    Trusting, serving ev'ry day;

    Just one glimpse of Him in glory

    Will the toils of life repay.
  \end{SBVerse}

  \begin{SBVerse}
    Onward to the prize before us!

    Soon His beauty we'll behold;

    Soon the pearly gates will open---

    We shall tread the streets of gold.
  \end{SBVerse}
\end{song}

\begin{song}{He Dies! He Dies!}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    He dies! He dies! The lowly Man of sorrows,

    On whom were laid our many griefs and woes;

    Our sins He bore, beneath God's awful billows,

    And He hath triumphed over all our foes.
  \end{SBVerse}

  \begin{SBOpGroup}
    I am He that liveth, that liveth and was dead,

    I am He that liveth, that liveth and was dead;

    And behold, I am alive forevermore,

    Behold, I am alive forevermore;

    I am He that liveth, that liveth and was dead,

    And behold, I am alive forevermore.
  \end{SBOpGroup}

  \begin{SBVerse}
    He lives! He lives! What glorious consolation!

    Exalted at His Father's own right hand,

    He pleads for us, and by His intercession,

    Enables all His saints by grace to stand.
  \end{SBVerse}

  \begin{SBVerse}
    He comes! He comes! O blest anticipation!

    In keeping with His true and faithful word;

    To call us to our heav'nly consummation---

    Caught up, to be ``forever with the Lord.''
  \end{SBVerse}
\end{song}

\begin{song}{I Am Waiting For The Dawning}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    I am waiting for the dawning

    Of that bright and glorious day,

    When the darksome night of sorrow

    Shall have vanished far away;

    When forever with the Saviour,

    Far beyond this vale of tears,

    I shall swell the hymn of worship

    Thru the everlasting years.
  \end{SBVerse}

  \begin{SBVerse}
    I am looking at the brightness,

    See, it shineth from afar,

    Of the clear and joyous beaming

    Of the Bright and Morning Star;

    Thru the dark grey mist of morning

    I behold its glorious light;

    Then away with ev'ry shadow

    Of this sad and weary night.
  \end{SBVerse}

  \begin{SBVerse}
    I am waiting for the coming

    Of the Lord who died for me;

    Oh, His words have thrilled my spirit,

    ``I will come again for thee.''

    Faith can almost hear Christ's footfall

    On the threshold of the door,

    And my heart, my heart is longing

    To be with Him evermore.
  \end{SBVerse}
\end{song}

\begin{song}{Safe In The Arms Of Jesus}{}
  {\SBPubDom}
  {Fanny Crosby}
  {}
  {}

  \begin{SBVerse}
    Safe in the arms of Jesus,

    Safe on His gentle breast,

    There by His love o'ershaded,

    Sweetly my soul shall rest.

    Hark! 'tis the voice of angels,

    Borne in a song to me,

    Over the fields of glory,

    Over the jasper sea.
  \end{SBVerse}

  \begin{SBOpGroup}
    Safe in the arms of Jesus,

    Safe on His gentle breast,

    There by His love o'ershaded,

    Sweetly my soul shall rest.
  \end{SBOpGroup}

  \begin{SBVerse}
    Safe in the arms of Jesus,

    Safe from corroding care,

    Safe from the world's temptations,

    Sin cannot harm me there.

    Free from the blight of sorrow,

    Free from my doubts and fears;

    Only a few more trials,

    Only a few more tears!
  \end{SBVerse}

  \begin{SBVerse}
    Jesus, my heart's dear refuge,

    Jesus has died for me;

    Firm on the Rock of Ages,

    Ever my trust shall be.

    Here let me wait in patience,

    Wait till the night is o'er;

    Wait till I see the morning

    Break on the golden shore.
  \end{SBVerse}
\end{song}

\begin{song}{All That Thrills My Soul Is Jesus}{}
  {\SBPubDom}
  {Thoro Harris}
  {}
  {}

  \begin{SBVerse}
    Who can cheer the heart like Jesus,

    By His presence all divine?

    True and tender, pure and precious,

    O how blest to call Him mine!
  \end{SBVerse}

  \begin{SBOpGroup}
    All that thrills my soul is Jesus,

    He is more than life to me;

    And the fairest of ten thousand

    In my blessed Lord I see.
  \end{SBOpGroup}

  \begin{SBVerse}
    Love of Christ so freely given,

    Grace of God beyond degree,

    Mercy higher than the heavens,

    Deeper than the deepest sea.
  \end{SBVerse}

  \begin{SBVerse}
    What a wonderful redemption!

    Never can a mortal know

    How my sin, tho' red like crimson,

    Can be whiter than the snow.
  \end{SBVerse}

  \begin{SBVerse}
    Ev'ry need His hand supplying,

    Ev'ry good in Him I see;

    On His strength divine relying,

    He is all in all to me.
  \end{SBVerse}

  \begin{SBVerse}
    By the crystal, flowing river

    With the ransomed I will sing,

    And forever and forever

    Praise and glorify the King.
  \end{SBVerse}
\end{song}

\begin{song}{Down From His Glory}{}
  {\SBPubDom}
  {William E. Booth-Clibborn}
  {}
  {}

  \begin{SBVerse}
    Down from His glory,

    Ever living story,

    My God and Savior came,

    And Jesus was His name.

    Born in a manger,

    To His own a stranger,

    A Man of sorrows, tears and agony.
  \end{SBVerse}

  \begin{SBOpGroup}
    O how I love Him! How I adore Him!

    My breath, my sunshine, my all in all!

    The great Creator became my Savior,

    And all God's fulness dwelleth in Him.
  \end{SBOpGroup}

  \begin{SBVerse}
    What condescension,

    Bringing us redemption;

    That in the dead of night,

    Not one faint hope in sight,

    God, gracious, tender,

    Laid aside His splendor,

    Stooping to woo, to win, to save my soul.
  \end{SBVerse}

  \begin{SBVerse}
    Without reluctance,

    Flesh and blood His substance

    He took the form of man,

    Revealed the hidden plan.

    O glorious myst'ry,

    Sacrifice of Calv'ry,

    And now I know Thou art the great ``I AM.''
  \end{SBVerse}
\end{song}

\begin{song}{Guide Me, O Thou Great Jehovah}{}
  {\SBPubDom}
  {William Williams}
  {}
  {}

  \begin{SBVerse}
    Guide me, O Thou great Jehovah,

    Pilgrim through this barren land.

    I am weak, but Thou art mighty;

    Hold me with Thy powerful hand.

    Bread of heaven,

    Feed me now and evermore.
  \end{SBVerse}

  \begin{SBVerse}
    Open now the crystal fountain,

    Whence the healing waters flow;

    Let the fire and cloudy pillar

    Lead me all my journey through.

    Strong Deliverer,

    Be Thou still my Strength and Shield.
  \end{SBVerse}

  \begin{SBVerse}
    When I tread the verge of Jordan,

    Bid my anxious fears subside;

    Death of death, and hell's destruction,

    Songs of praises,

    I will ever give to Thee.
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{Through My Hand No Nail Is Driven}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    Through my hand no nail is driven,

    On my brow no thorns are worn,

    In my side there is no spear-wound---

    Jesus all my sins hath borne.
  \end{SBVerse}

  \begin{SBVerse}
    His the nails relentless driven,

    Mine the peace by Him procured;

    For this soul with sin so burdened,

    Freed in mercy---love allured.
  \end{SBVerse}

  \begin{SBVerse}
    His the crown of thorns sharp-piercing,

    Mine the peace for aye to last;

    Mine the crown of fadeless glory

    At His blessed feet to cast.
  \end{SBVerse}

  \begin{SBVerse}
    His the spear His dear side wounding,

    Mine the peace with God thus made,

    Sinless He---and yet sin-bearing---

    All our sins on Him were laid.
  \end{SBVerse}

  \begin{SBVerse}
    'Neath Thy cross I stand and worship,

    Suffering man, yet conquering God!

    Resting on Thy death-atonement,

    Weary, I lay down my load.
  \end{SBVerse}

  \begin{SBVerse}
    Cease, my soul, thy restless striving;

    Christ's atoning work is done;

    Seek to run the race with patience,

    At the cross in faith begun.
  \end{SBVerse}
\end{song}

\begin{song}{It Was Down At The Feet Of Jesus}{}
  {\SBPubDom}
  {}
  {}
  {}

  \begin{SBVerse}
    It was down at the feet of Jesus,

    O the happy, happy day!

    That my soul found peace in believing,

    And my sins were washed away.
  \end{SBVerse}

  \begin{SBOpGroup}
    Let me tell the old, old story

    Of His grace so full and free;

    For I feel like giving Him the glory

    For His wondrous love to me.
  \end{SBOpGroup}

  \begin{SBVerse}
    It was down at the feet of Jesus,

    Where I found such perfect rest,

    Where the light first dawned on my spirit,

    And my soul was truly blest.
  \end{SBVerse}

  \begin{SBVerse}
    It was down at the feet of Jesus,

    Where I brought my guilt and sin,

    That He cancelled all my transgressions

    And salvation entered in.
  \end{SBVerse}
\end{song}

\begin{song}{Leaning On The Everlasting Arms}{}
  {\SBPubDom}
  {Elisha A. Hoffman}
  {}
  {}

  \begin{SBVerse}
    What a fellowship, what a joy divine,

    Leaning on the everlasting arms;

    What a blessedness, what a peace is mine,

    Leaning on the everlasting arms.
  \end{SBVerse}

  \begin{SBOpGroup}
    Leaning, leaning,

    Safe and secure from all alarms;

    Leaning, leaning,

    Leaning on the everlasting arms.
  \end{SBOpGroup}

  \begin{SBVerse}
    O how sweet to walk in this pilgrim way,

    Leaning on the everlasting arms;

    O how bright the path grows from day to day,

    Leaning on the everlasting arms.
  \end{SBVerse}

  \begin{SBVerse}
    What have I to dread, what have I to fear,

    Leaning on the everlasting arms?

    I have blessed peace with my Lord so near,

    Leaning on the everlasting arms.
  \end{SBVerse}
\end{song}

\WBColBrk

\begin{song}{Nearer, My God, To Thee}{}
  {\SBPubDom}
  {Sarah Flower Adams}
  {}
  {}

  \begin{SBVerse}
    Nearer, my God, to Thee, nearer to Thee!

    E'en though it be a cross that raiseth me,

    Still all my song shall be,

    Nearer, my God, to Thee;

    Nearer, my God, to Thee, nearer to Thee!
  \end{SBVerse}

  \begin{SBVerse}
    Though like the wanderer, the sun gone down,

    Darkness be over me, my rest a stone;

    Yet in my dreams I'd be

    Nearer, my God, to Thee;

    Nearer, my God, to Thee, nearer to Thee!
  \end{SBVerse}

  \begin{SBVerse}
    There let the way appear, steps unto heaven;

    All that Thou sendest me, in mercy given;

    Angels to beckon me

    Nearer, my God, to Thee;

    Nearer, my God, to Thee, nearer to Thee!
  \end{SBVerse}

  \begin{SBVerse}
    Then, with my waking thoughts bright with Thy praise,

    Out of my stony griefs Bethel I'll raise;

    So by my woes to be

    Nearer, my God, to Thee;

    Nearer, my God, to Thee, nearer to Thee!
  \end{SBVerse}

  \begin{SBVerse}
    Or if, on joyful wing cleaving the sky,

    Sun, moon, and stars forgot, upward I fly,

    Still all my song shall be,

    Nearer, my God, to Thee;

    Nearer, my God, to Thee, nearer to Thee!
  \end{SBVerse}
\end{song}

\begin{song}{O Love That Will Not Let Me Go}{}
  {\SBPubDom}
  {George Matheson}
  {}
  {}

  \begin{SBVerse}
    O love that will not let me go,

    I rest my weary soul in Thee;

    I give Thee back the life I owe,

    That in Thine ocean depths its flow

    May richer, fuller be.
  \end{SBVerse}

  \begin{SBVerse}
    O Light that follows all my way,

    I yield my flick'ring torch to Thee;

    My heart restores its borrowed ray,

    That in Thy sunshine's blaze its day

    May brighter, fairer be.
  \end{SBVerse}

  \begin{SBVerse}
    O Joy that seekest me thru' pain,

    I cannot close my heart to Thee;

    I trace the rainbow thru' the rain

    And feel the promise is not vain

    That morn shall tearless be.
  \end{SBVerse}

  \begin{SBVerse}
    O cross that liftest up my head,

    I dare not ask to fly from Thee;

    I lay in dust life's glory dead,

    And from the ground there blossoms red

    Life that shall endless be.
  \end{SBVerse}
\end{song}

\begin{song}{Praise Him! Praise Him!}{}
  {\SBPubDom}
  {Fanny Crosby}
  {}
  {}

  \begin{SBVerse}
    Praise Him! Praise Him! Jesus, our blessed Redeemer!

    Sing, O earth---His wonderful love proclaim!

    Hail Him! Hail Him! Highest archangels in glory;

    Strength and honor give to His holy name!

    Like a shepherd, Jesus will guard His children;

    In His arms He carries them all day long.
  \end{SBVerse}

  \begin{SBOpGroup}
    Praise Him! Praise Him! Tell of His excellent greatness.

    Praise Him! Praise Him ever in joyful song!
  \end{SBOpGroup}

  \begin{SBVerse}
    Praise Him, praise Him! Jesus, our blessed Redeemer!

    For our sins He suffered, and bled, and died.

    He, our Rock, our Hope of eternal salvation---

    Hail Him! Hail Him! Jesus, the Crucified!

    Sound His praises! Jesus, who bore our sorrows!

    Love unbounded, wonderful, deep, and strong.
  \end{SBVerse}

  \begin{SBVerse}
    Praise Him! Praise Him! Jesus, our blessed Redeemer!

    Heav'nly portals loud with hosannas ring!

    Jesus, Savior, reigneth forever and ever.

    Crown Him! Crown Him! Prophet, and Priest, and King!

    Christ is coming, over the world victorious;

    Pow'r and glory unto the Lord belong!
  \end{SBVerse}
\end{song}

\begin{song}{The Old Rugged Cross}{}
  {\SBPubDom}
  {George Bennard}
  {}
  {}

  \begin{SBVerse}
    On a hill far away stood an old rugged cross,

    The emblem of suffering and shame;

    And I love that old cross where the dearest and best

    For a world of lost sinners was slain.
  \end{SBVerse}

  \begin{SBOpGroup}
    So I'll cherish the old rugged cross,

    Till my trophies at last I lay down;

    I will cling to the old rugged cross,

    And exchange it some day for a crown.
  \end{SBOpGroup}

  \begin{SBVerse}
    O that old rugged cross, so despised by the world,

    Has a wondrous attraction for me;

    For the dear Lamb of God left His glory above

    To bear it to dark Calvary.
  \end{SBVerse}

  \begin{SBVerse}
    In that old rugged cross, stained with blood so divine,

    A wondrous beauty I see,

    For 'twas on that old cross Jesus suffered and died,

    To pardon and sanctify me.
  \end{SBVerse}

  \begin{SBVerse}
    To that old rugged cross I will ever be true,

    Its shame and reproach gladly bear;

    Then He'll call me some day to my home far away,

    Where His glory forever I'll share.
  \end{SBVerse}
\end{song}

\begin{song}{Christ Returneth}{}
  {\SBPubDom}
  {H.L. Turner}
  {}
  {}

  \begin{SBVerse}
    It may be at morn, when the day is awaking,

    When sunlight thro' darkness and shadow is breaking,

    That Jesus will come in the fullness of glory;

    To receive from the world His own.
  \end{SBVerse}

  \begin{SBOpGroup}
    O Lord Jesus, how long, how long

    Ere we shout the glad song.

    Christ returneth! Hallelujah!

    Hallelujah! Amen,

    Hallelujah! Amen.
  \end{SBOpGroup}

  \begin{SBVerse}
    It may be at midday, it may be at twilight,

    It may be, perchance, that the blackness of midnight

    Will burst into light in the blaze of His glory,

    When Jesus receives His own.
  \end{SBVerse}

  \begin{SBVerse}
    While hosts cry Hosanna, from heaven descending,

    With glorified saints and the angels attending,

    With grace on His brow, like a halo of glory,

    Will Jesus receive His own.
  \end{SBVerse}

  \begin{SBVerse}
    O joy! O delight! Should we go without dying,

    No sickness, no sadness, no dread and no crying,

    Caught up thro' the clouds with our Lord into glory,

    When Jesus receives His own.
  \end{SBVerse}
\end{song}

% \WBColBrk

\begin{song}{'Tis So Sweet To Trust In Jesus}{}
  {\SBPubDom}
  {Louisa M.R. Stead}
  {}
  {}

  \begin{SBVerse}
    'Tis so sweet to trust in Jesus,

    And to take Him at His word;

    Just to rest upon His promise,

    And to know, ``Thus saith the Lord.''
  \end{SBVerse}

  \begin{SBOpGroup}
    Jesus, Jesus, how I trust Him!

    How I've proved Him o'er and o'er!

    Jesus, Jesus, precious Jesus!

    O for grace to trust Him more!
  \end{SBOpGroup}

  \begin{SBVerse}
    O how sweet to trust in Jesus,

    Just to trust His cleansing blood;

    And in simple faith to plunge me

    'Neath the healing, cleansing flood!
  \end{SBVerse}

  \begin{SBVerse}
    Yes, 'tis sweet to trust in Jesus,

    Just from sin and self to cease;

    Just from Jesus simply taking

    Life and rest, and joy and peace.
  \end{SBVerse}
\end{song}

\begin{song}{Shout To The Lord}{}
  {}
  {Darlene Zschech}
  {}
  {}

  \begin{SBVerse}
    My Jesus, my Savior

    Lord there is none like You

    All of my days, I want to praise

    The wonders of Your mighty love

    My Comfort, my Shelter

    Tower of Refuge and Strength

    Let every breath, all that I am

    Never cease to worship You
  \end{SBVerse}

  \begin{SBOpGroup}
    Shout to the Lord All the earth let us sing

    Power and majesty Praise to the King

    Mountains bow down And the sea will roar

    At the sound of Your Name

    I sing for joy at the work of Your hands

    Forever I'll love You, forever I'll stand

    Nothing compares to The promise I have in You.
  \end{SBOpGroup}
\end{song}

\begin{song}{Yet Not I But Through Christ In Me}{}
  { CityAlight}
  {CityAlight}
  {}
  {}

  \begin{SBVerse}
    What gift of grace is Jesus my redeemer

    There is no more for heaven now to give

    He is my joy, my righteousness, and freedom

    My steadfast love, my deep and boundless peace
  \end{SBVerse}

  \begin{SBOpGroup}
    To this I hold, my hope is only Jesus

    For my life is wholly bound to his

    Oh how strange and divine, I can sing: all is mine!

    Yet not I, but through Christ in me
  \end{SBOpGroup}

  \begin{SBVerse}
    The night is dark but I am not forsaken

    For by my side, the Saviour He will stay

    I labour on in weakness and rejoicing

    For in my need, His power is displayed
  \end{SBVerse}

  \begin{SBOpGroup}
    To this I hold, my Shepherd will defend me

    Through the deepest valley He will lead

    Oh the night has been won, and I shall overcome!

    Yet not I, but through Christ in me
  \end{SBOpGroup}

  \begin{SBVerse}
    No fate I dread, I know I am forgiven

    The future sure, the price it has been paid

    For Jesus bled and suffered for my pardon

    And He was raised to overthrow the grave
  \end{SBVerse}

  \begin{SBOpGroup}
    To this I hold, my sin has been defeated

    Jesus now and ever is my plea

    Oh the chains are released, I can sing: I am free!

    Yet not I, but through Christ in me
  \end{SBOpGroup}

  \begin{SBVerse}
    With every breath I long to follow Jesus

    For He has said that He will bring me home

    And day by day I know He will renew me

    Until I stand with joy before the throne
  \end{SBVerse}

  \begin{SBOpGroup}
    To this I hold, my hope is only Jesus

    All the glory evermore to Him

    When the race is complete, still my lips shall repeat:

    Yet not I, but through Christ in me!
  \end{SBOpGroup}
  \begin{SBOpGroup}
    When the race is complete, still my lips shall repeat:

    Yet not I, but through Christ in me!

    Yet not I, but through Christ in me!

    Yet not I, but through Christ in me!
  \end{SBOpGroup}
\end{song}

\end{document}
\bye
%
%%%
% Document ends.
%%%
